---
title: "SEAS Study 1 Main Analyses"
author:
  name: Siobhan Crowley
date: 01/18/2026
format: html
editor_options: 
  chunk_output_type: console
---

Analyses for Study 1 of the Social Exclusion and Status Study. See our [pre-registration](https://doi.org/10.17605/OSF.IO/SF5G7) for more details.

# Packages
```{r packages, message = FALSE, warning = FALSE}
library(readxl)
library(tidyverse)
library(lme4)
library(effsize)
library(showtext)
library(viridis)

showtext_auto()
```

# Data Preparation
```{r data-load}
seas_full <- read_excel("../Data/FINAL SEAS V1 Dataset.xlsx")

seas <- filter(seas_full, final_data == "Y") #filtering out excluded participants
```

```{r data-prep}
seas <- seas |>
  mutate(
    DOB = make_date(birth_year, birth_month, birth_day), #creating date of birth and date of test columns
    DOT = as_date(DOT),
    .before = DOT
  ) |>
  mutate(
    age_months = interval(DOB, DOT) %/% months(1), .after = DOT #calculating age in months
  )
```

```{r data-colors}
magma_colors <- c("#000004FF", "#180F3EFF", "#451077FF", "#721F81FF", "#9F2F7FFF", "#CD4071FF", "#F1605DFF", "#FD9567FF", "#FEC98DFF", "#FCFDBFFF") #from magma(10)
```

# Demographics
```{r demo}
full_count <- nrow(seas_full)

full_count_nopilot <- seas_full |>
  filter(str_detect(subject, "^SEAS-._P..$", negate = TRUE)) |> #excluding pilot participants
  nrow()

#Gender
gender_count <- seas |>
  group_by(gender) |>
  summarise(n = n())

#Age
age_count <- seas |>
  group_by(age) |>
  summarise(n = n())

#Race/Ethnicity
identity_count <- seas |>
  mutate(
    identity = if_else(str_length(identity) > 3, "MX", identity) #Re-classifying anyone with more than one selection as "mixed race"
  ) |>
  group_by(identity) |>
  summarise(n = n()) |>
  arrange(desc(n))
```

`r full_count_nopilot` children participated in the study, and there are `r nrow(seas)` participants in the final SEAS dataset, `r gender_count$n[1]` boys and `r gender_count$n[2]` girls. 

There are `r age_count$n[1]` 3-year-olds, `r age_count$n[2]` 4-year-olds, `r age_count$n[3]` 5-year-olds, and `r age_count$n[4]` 6-year-olds (`r age_count$n[1] + age_count$n[2]` in the 3-4 group and `r age_count$n[3] + age_count$n[4]` in the 5-6 group).

And there are `r identity_count$n[1]` participants who identify as White or European American, `r identity_count$n[2]` as Asian, `r identity_count$n[4]` as Middle Eastern or North African, `r identity_count$n[6]` as Hispanic, Latino/Latina/Latinx, or Spanish, and `r identity_count$n[3] + identity_count$n[5]` as multiple races or another race/ethnicity not listed. There are 0 participants who identify as Native Hawaiian or Pacific Islander, and 0 as American Indian or Alaska Native.


# 1. Do children correctly identify the social excluder?

```{r identify-prep}
#Convert memory check results to numeric and calculate sum score
seas <- seas |>
  mutate(
    mem_check_1 = if_else(mem_check_1 == "correct", 1, 0),
    mem_check_2 = if_else(mem_check_2 == "correct", 1, 0),
    mem_check_3 = if_else(mem_check_3 == "correct", 1, 0),
    mem_check_4 = if_else(mem_check_4 == "correct", 1, 0),
    mem_check_total = mem_check_1 + mem_check_2 + mem_check_3 + mem_check_4
  )
```

### Preliminary Analysis
```{r identify-glmm}
#Pivoting to examine trial-by-trial
mem_check_pivoted <- seas |>
  select(subject, gender, siblings, age_months, starts_with("type"), starts_with("mem_check")) |>
  pivot_longer(
    cols = c(starts_with("type"), matches("mem_check_.$")), 
    names_to = c(".value", "trial"),
    names_pattern = "(.*)_(.)$"
    ) |>
  rename(response = mem_check)

#Binomial GLMM

# summary(glmer(
#   response ~ trial + type + siblings + gender + age_months + (1 | subject),
#   data = mem_check_pivoted,
#   family = "binomial"
# )) #rank-deficient and failed to converge


identify_glmm <- summary(glmer(
  response ~ trial + gender + age_months + (1 | subject),
  data = mem_check_pivoted,
  family = "binomial"
)) #removed type and siblings in order to converge

identify_glmm
```

To assess other factors that may potentially affect participants' performance on memory check questions, we created a generalized linear mixed model (GLMM) with a binomial family, using trial, type (cyber, animals, playdoh, and trampoline), siblings, gender, and age in months as predictors. This model failed to converge, so we removed type and then siblings. Of the remaining variables assessed, the only element that was found significant was age, with a z value of `r round(identify_glmm$coefficients[6,3], 2)` and a p-value of `r signif(identify_glmm$coefficients[6,4], 2)`.

```{r identify-age-scatter}
identify_age_scatter <- seas |>
  ggplot(aes(x = age_months, y = mem_check_total)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 2, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Memory Check Performance",
    x = "Age (Months)",
    y = "Correct Memory Responses"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  coord_cartesian(ylim = c(0, 4))


identify_age_scatter
```

### Main Analysis
```{r identify-ttest}
identify_ttest <- t.test(seas$mem_check_total, mu = 2)
identify_ttest
identify_d <- cohen.d(seas$mem_check_total, f = NA, mu = 2)
```

We performed a t-test to assess whether participants' summed memory check scores were statistically different from chance, finding that the t statistic was equal to `r round(unname(identify_ttest$statistic), 2)` and the p-value was `r signif(unname(identify_ttest$p.value), 2)`, demonstrating that children were able to correctly recall the events of the scenarios. Cohen's d was `r round(unname(identify_d$estimate), 2)`, which is considered a `r as.character(identify_d$magnitude)` effect size.

```{r identify-box}
identify_boxplot <- seas |>
  ggplot(aes(x = as.factor(age), y = mem_check_total, fill = as.factor(age))) +
  geom_boxplot(fill = c(magma_colors[3], magma_colors[5], magma_colors[7], magma_colors[9])) +
  geom_hline(yintercept = 2, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Memory Check Performance by Age",
    x = "Age (Years)",
    y = "Correct Memory Responses"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  coord_cartesian(ylim = c(0, 4))

identify_boxplot
```

```{r identify-col}
identify_column <- seas |>
  ggplot(aes(x = as.factor(age), y = mem_check_total)) +
  stat_summary(
    fun = "mean",
    geom = "bar",
    position = position_dodge(width = 0.9),
    fill = "#CD4071FF"
  ) +
  stat_summary(
    fun.data = "mean_cl_normal",
    geom = "errorbar",
    width = 0.2,
    linewidth = 0.5,
    position = position_dodge(width = 0.9)
  ) +
  labs(
    title = "Study 1 Memory Check Performance by Age",
    x = "Age (Years)",
    y = "Correct Memory Responses"
  ) +
  geom_hline(yintercept = 2, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25),
        ) +
    scale_y_continuous(breaks = c(0, 1, 2, 3, 4))

identify_column
```

# 2. Do children use information about social exclusion to determine who is in charge?

## Hypothesis 1 
We expect that children will think that social excluders are in charge more often than they will think excluded characters are in charge.

```{r status-prep}
#Convert excluder/excluded selection to numeric and calculate sum score
seas <- seas |>
  mutate(
    status_1 = if_else(status_1 == "excluder", 1, 0),
    status_2 = if_else(status_2 == "excluder", 1, 0),
    status_3 = if_else(status_3 == "excluder", 1, 0),
    status_4 = if_else(status_4 == "excluder", 1, 0),
    status_total = status_1 + status_2 + status_3 + status_4
  )
```

### Preliminary Analysis
```{r status-glmm}
#Pivoting to examine trial-by-trial
status_pivoted <- seas |>
  select(subject, gender, siblings, age, age_months, mem_check_total, starts_with("type"), matches("status_.$")) |>
  pivot_longer(
    cols = c(starts_with("type"), matches("status_.$")), 
    names_to = c(".value", "trial"),
    names_pattern = "(.*)_(.)$"
    ) |>
  rename(response = status)

#Binomial GLMM

# summary(glmer(
#   response ~ trial + type + gender + siblings + age_months + (1 | subject),
#   data = status_pivoted,
#   family = "binomial"
# )) #rank-deficient and other error messages; still does not converge when only trial and age_months included--I tried the categorical age variable as well, and it still did not converge

status_trial_glmm <- summary(glmer(
  response ~ trial + (1 | subject),
  data = status_pivoted,
  family = "binomial"
)) 

status_trial_glmm

status_age_glmm <- summary(glmer(
  response ~ age_months + (1 | subject),
  data = status_pivoted,
  family = "binomial"
)) 

status_age_glmm
```

To assess other factors that may potentially affect participants' performance on memory check questions, we created a generalized linear mixed model (GLMM) with a binomial family, using trial, type (cyber, animals, playdoh, and trampoline), siblings, gender, and age in months as predictors. This model failed to converge, so all variables except trial and age_months were removed; this also did not converge, so we tried to substitue a categorical age variable (3-6) in the same model, but this still did not converge. Therefore, we ran two different GLMMs, one for trial and one for age. In the trial model, only trial 3 (i.e. the first story) was significant (z = `r round(status_trial_glmm$coefficients[3,3], 2)`, p = `r signif(status_trial_glmm$coefficients[3,4], 2)`). The GLMM examining age in months was not significant.

### Main Analysis
```{r status-ttest}
status_ttest <- t.test(seas$status_total, mu = 2)
status_ttest
```

In this one-sample t-test, the t statistic was equal to `r round(unname(status_ttest$statistic), 2)` and the p-value `r round(unname(status_ttest$p.value), 2)`, demonstrating that participants did not select the excluder as being in charge more often than chance.

## Hypothesis 2
We expect that age will be significantly related to children's identification of who is in charge.

### Main Analysis
```{r status-age-lm}
#Linear model with age
status_age_lm <- summary(lm(
  status_total ~ age_months,
  data = seas
))

status_age_lm
```

In this linear model of the number of times the excluder was selected as in charge with age in months as a predictor, the t value was `r round(status_age_lm$coefficients[2, 3], 2)` and the p-value was `r round(status_age_lm$coefficients[2, 4], 2)`, demonstrating that age did not significantly influence the number of times the excluder was selected as in charge.

```{r status-box}
status_age_boxplot <- seas |>
  ggplot(aes(x = as.factor(age), y = status_total, fill = as.factor(age))) +
  geom_boxplot(fill = c(magma_colors[3], magma_colors[5], magma_colors[7], magma_colors[9])) +
  geom_hline(yintercept = 2, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Excluder Status Selection",
    x = "Age (Years)",
    y = "Excluder Selection"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )

status_age_boxplot
```

```{r status-col}
status_column <- seas |>
  ggplot(aes(x = as.factor(age), y = status_total)) +
  stat_summary(
    fun = "mean",
    geom = "bar",
    position = position_dodge(width = 0.9),
    fill = "#CD4071FF"
  ) +
  stat_summary(
    fun.data = "mean_cl_normal",
    geom = "errorbar",
    width = 0.2,
    linewidth = 0.5,
    position = position_dodge(width = 0.9)
  ) +
  labs(
    title = "Study 1 Status Excluder Selection by Age",
    x = "Age (Years)",
    y = "Excluder Selection"
  ) +
  geom_hline(yintercept = 2, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25),
        ) +
    scale_y_continuous(breaks = c(0, 1, 2, 3, 4)) +
  coord_cartesian(ylim = c(0, 4))

status_column
```

```{r status-scatter}
status_scatter <- seas |>
  ggplot(aes(x = age_months, y = status_total)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 2, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Excluder Status Selection",
    x = "Age (Months)",
    y = "Excluder Selection"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  coord_cartesian(ylim = c(0, 4))


status_scatter
```

# 3. Do children use information about social exclusion to determine who has more physical and social resources?

## Hypothesis 1
We expect that children will identify the excluder as having more resources.

```{r resource-prep}
#Convert excluder resource selection to numeric and calculate sum score
seas <- seas |>
  mutate(
    resource_1 = if_else(resource_1 == "excluder", 1, 0, NA), #One participant who did not answer the first resource question
    resource_2 = if_else(resource_2 == "excluder", 1, 0),
    resource_3 = if_else(resource_3 == "excluder", 1, 0),
    resource_4 = if_else(resource_4 == "excluder", 1, 0),
    resource_total = resource_1 + resource_2 + resource_3 + resource_4
  )

#Physical and social resources sum scores
seas <- seas |>
  mutate(
    resource_physical = case_when(
      resource_type_1 == "physical" ~ resource_1,
      resource_type_2 == "physical" ~ resource_2
    ),
    resource_social = case_when(
      resource_type_1 == "social" ~ resource_1,
      resource_type_2 == "social" ~ resource_2
    )
  ) |>
  mutate(
    resource_physical = case_when(
      resource_type_3 == "physical" ~ resource_physical + resource_3,
      resource_type_4 == "physical" ~ resource_physical + resource_4
    ),
    resource_social = case_when(
      resource_type_3 == "social" ~ resource_social + resource_3,
      resource_type_4 == "social" ~ resource_social + resource_4
    )
  )
```

### Preliminary Analysis
```{r resource-glmm}
#Pivoting to examine trial-by-trial
resource_pivoted <- seas |>
  select(subject, gender, siblings, age_months, starts_with("type"), matches("resource_type_.$"), matches("resource_.$")) |>
  pivot_longer(
    cols = c(starts_with("type"), starts_with("resource")), 
    names_to = c(".value", "trial"),
    names_pattern = "(.*)_(.)$"
    ) |>
  rename(response = resource)

#Binomial GLMM

# summary(glmer(
#   response ~ trial + type + resource_type + gender + siblings + age_months + (1 | subject),
#   data = resource_pivoted,
#   family = "binomial"
# )) #rank-deficient; needs type and siblings removed to converge

resource_glmm <- summary(glmer(
  response ~ trial + resource_type + gender + age_months + (1 | subject),
  data = resource_pivoted,
  family = "binomial"
))

resource_glmm
```

In this GLMM, type and siblings had to be removed in order for the model to converge. Of those included, each trial was significant (Trial 2: z = `r round(resource_glmm$coefficients[2, 3], 2)`, p = `r signif(resource_glmm$coefficients[2, 4], 2)`; Trial 3: z = `r round(resource_glmm$coefficients[3, 3], 2)`, p = `r signif(resource_glmm$coefficients[3, 4], 2)`; Trial 4: z = `r round(resource_glmm$coefficients[4, 3], 2)`, p = `r signif(resource_glmm$coefficients[4, 4], 2)`), as was age in months (z = `r round(resource_glmm$coefficients[7, 3], 2)`, p = `r signif(resource_glmm$coefficients[7, 4], 2)`), so that participants became more likely to select the excluder as having more resources as they progressed further into the study and as they got older.

### Main Analysis
```{r resource-ttest}
resource_ttest <- t.test(seas$resource_total, mu = 2)
physical_ttest <- t.test(seas$resource_physical, mu = 1)
social_ttest <- t.test(seas$resource_social, mu = 1)

resource_ttest
physical_ttest
social_ttest

resource_d <- cohen.d(seas$resource_total, f = NA, mu = 2, na.rm = TRUE)
physical_d <- cohen.d(seas$resource_physical, f = NA, mu = 1, na.rm = TRUE) 
social_d <- cohen.d(seas$resource_social, f = NA, mu = 1)
```

In this one-sample t-test of overall resources, the t statistic was `r round(unname(resource_ttest$statistic), 2)`, with a p-value of `r signif(unname(resource_ttest$p.value), 2)` and a Cohen's d of `r round(unname(resource_d$estimate), 2)` (`r as.character(resource_d$magnitude)`), demonstrating that children chose the excluder as having more resources more often than chance. 

These results hold when physical and social resources are examined separately. A t-test exploring the former produces a t statistic of `r round(unname(physical_ttest$statistic), 2)` and a p-value of `r signif(unname(social_ttest$p.value), 2)` with a Cohen's d of `r round(unname(physical_d$estimate), 2)` (`r as.character(physical_d$magnitude)`).

A t-test examining only social resources resulted in a t of `r round(unname(social_ttest$statistic), 2)` and a p-value of `r signif(unname(physical_ttest$p.value), 2)`, with a Cohen's d of `r round(unname(social_d$estimate), 2)` (`r as.character(social_d$magnitude)`).

## Hypothesis 2
Older children will be more likely to identify excluders as controlling resources than younger children.

### Main Analysis
```{r resource-age-lm}
#Linear models with age
#Total resources
resource_age_lm <- summary(lm(
  resource_total ~ age_months,
  data = seas
))

resource_age_lm

#Physical resources
physical_age_lm <- summary(lm(
  resource_physical ~ age_months,
  data = seas
))

physical_age_lm

#Social resources
social_age_lm <- summary(lm(
  resource_social ~ age_months,
  data = seas
))

social_age_lm
```

In a linear model with only age, age significantly influenced resource selection (t = `r round(resource_age_lm$coefficients[2, 3], 2)`, p = `r signif(resource_age_lm$coefficients[2, 4], 2)`. When examining physical and social resources separately, age was on the border of significance for physical resources (t = `r round(physical_age_lm$coefficients[2, 3], 2)` and p = `r signif(physical_age_lm$coefficients[2, 4], 2)`) and social resources was significant (t = `r round(social_age_lm$coefficients[2, 3], 2)` and p = `r signif(social_age_lm$coefficients[2, 4], 2)`).

```{r resource-scatter}
resource_age_scatter <- seas |>
  filter(!is.na(resource_total)) |>
  ggplot(aes(x = age_months, y = resource_total)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 2, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Excluder Resource Selection by Age",
    x = "Age (Months)",
    y = "Excluder Selection"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )

resource_age_scatter
```

```{r resource-scatter-physsoc}
resource_scatter_physsoc <- seas |>
  pivot_longer(
    cols = resource_physical:resource_social,
    names_to = "type",
    names_pattern = "resource_(.*)",
    values_to = "excluder_select"
  ) |>
  filter(!is.na(excluder_select)) |>
  ggplot(aes(x = age_months, y = excluder_select, color = type, fill = type)) +
  geom_point(position = position_jitter(height = 0.1)) +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    alpha = 0.25) +
  geom_hline(yintercept = 1, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  scale_color_manual(
    values = c(magma_colors[3], magma_colors[7]), 
    labels = c("Physical", "Social")) +
  scale_fill_manual(
    values = c(magma_colors[3], magma_colors[7]),
    labels = c("Physical", "Social")) +
  labs(
    title = "Study 1 Excluder Resource Selection by Age",
    x = "Age (Months)",
    y = "Excluder Selection",
    color = NULL,
    fill = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    plot.caption = element_text(hjust = 0.5),
    text = element_text(family = "serif", size = 25),
    legend.position = "top"
        ) +
  scale_y_continuous(
    breaks = c(0, 1, 2))

resource_scatter_physsoc
```

```{r resource-box}
#Total resources
resource_age_boxplot <- seas |>
  filter(!is.na(resource_total)) |>
  ggplot(aes(x = as.factor(age), y = resource_total, fill = as.factor(age))) +
  geom_boxplot(fill = c(magma_colors[3], magma_colors[5], magma_colors[7], magma_colors[9])) +
  labs(
    title = "Study 1 Excluder Resource Selection",
    x = "Age (Years)",
    y = "Excluder Selection"
  ) +
  geom_hline(yintercept = 2, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )

resource_age_boxplot

#Physical and social resources
physsoc_age_boxplot <- seas |>
  pivot_longer(c("resource_physical", "resource_social"), names_to = "resource_total_type", names_pattern = ".*_(.*)", values_to = "excluder_select") |>
  filter(!is.na(excluder_select)) |>
  ggplot(aes(x = as.factor(age), y = excluder_select, fill = resource_total_type)) +
  geom_boxplot(
    position = "dodge") +
  labs(
    title = "Study 1 Excluder Resource Selection",
    x = "Age (Years)",
    y = "Excluder Selection",
    fill = NULL
  ) +
  geom_hline(yintercept = 1, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  scale_fill_manual(
    values = c(magma_colors[3], magma_colors[7]),
    labels = c("Physical", "Social")) +
  theme_minimal() +
  theme(
    legend.position = "top",
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
    scale_y_continuous(breaks = c(0, 1, 2))

physsoc_age_boxplot
```

```{r resource-col}
resource_column <- seas |>
  pivot_longer(c("resource_physical", "resource_social"), names_to = "resource_total_type", names_pattern = ".*_(.*)", values_to = "excluder_select") |> 
  filter(!is.na(excluder_select)) |>
  ggplot(aes(x = as.factor(age), y = excluder_select, fill = resource_total_type)) +
  stat_summary(
    fun = "mean",
    geom = "bar",
    position = position_dodge(width = 0.9)
  ) +
  stat_summary(
    fun.data = "mean_cl_normal",
    geom = "errorbar",
    width = 0.2,
    linewidth = 0.5,
    position = position_dodge(width = 0.9)
  ) +
  labs(
    title = "Study 1 Excluder Resource Selection",
    x = "Age (Years)",
    y = "Excluder Selection",
    fill = NULL
  ) +
  geom_hline(yintercept = 1, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  scale_fill_manual(
    values = c(magma_colors[3], magma_colors[7]),
    labels = c("Physical", "Social")) +
  theme_minimal() +
  theme(
    legend.position = "top",
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
    scale_y_continuous(breaks = c(0, 1, 2))

resource_column
```