---
title: "02 SEAS Study 1 Explanatory Analyses"
format: html
author: Siobhan Crowley
date: 04/12/2026
editor: source
editor_options: 
  chunk_output_type: console
---

# Packages
```{r packages, message = FALSE, warning = FALSE}
library(readxl)
library(tidyverse)
library(lme4)
library(lmerTest)
library(showtext)
library(viridis)
library(chisq.posthoc.test)
library(Hmisc)
library(gt)
library(webshot2)

showtext_auto()
```

# Data Preparation
```{r data-colors}
magma_colors <- c("#000004FF", "#180F3EFF", "#451077FF", "#721F81FF", "#9F2F7FFF", "#CD4071FF", "#F1605DFF", "#FD9567FF", "#FEC98DFF", "#FCFDBFFF") #from magma(10)

wo_black <- viridis::magma(20)[5:20]
```

```{r data-load}
seas_full <- read_excel("../Data/FINAL SEAS V1 Dataset.xlsx")

seas <- filter(seas_full, final_data == "Y") #filtering out excluded participants
```

```{r data-init-prep}
seas <- seas |>
  mutate(
    DOB = make_date(birth_year, birth_month, birth_day), #creating date of birth and date of test columns
    DOT = as_date(DOT),
    .before = DOT
  ) |>
  mutate(
    age_months = interval(DOB, DOT) %/% months(1), .after = DOT #calculating age in months
  )
```

```{r data-main-prep}
#Combining any explanation code for a particular response
seas_united <- seas |>
  unite("status_explain_1", status_storyref_1:status_relation_1, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_1", resource_storyref_1:resource_relation_1, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_2", status_storyref_2:status_relation_2, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_2", resource_storyref_2:resource_relation_2, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_3", status_storyref_3:status_relation_3, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_3", resource_storyref_3:resource_relation_3, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_4", status_storyref_4:status_relation_4, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_4", resource_storyref_4:resource_relation_4, sep  = " ", na.rm = TRUE)
```

```{r explain-map-func}
#Creating a general explanation mapping function
individual_explain_func <- function(status_or_resource, trial_num) {
  
  possible_explain <- c("ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")
  
  column_of_interest <- paste0(status_or_resource, "_explain_", trial_num)
  
  list_of_dfs <- purrr::map(possible_explain, function(explain) {
    seas_united |>
      mutate(!!paste0(status_or_resource, "_", explain, "_", trial_num) := if_else(str_detect(.data[[column_of_interest]], explain), 1, 0))
  })
    
    selected_cols <- map(list_of_dfs, ~select(., subject, last_col()))
    
    reduce(selected_cols, left_join, by = "subject")
  }
```

```{r explain-columns}
#Gathering individual explanation columns for each response
seas_status_1 <- individual_explain_func("status", 1)
seas_resource_1 <- individual_explain_func("resource", 1)
seas_status_2 <- individual_explain_func("status", 2)
seas_resource_2 <- individual_explain_func("resource", 2)
seas_status_3 <- individual_explain_func("status", 3)
seas_resource_3 <- individual_explain_func("resource", 3)
seas_status_4 <- individual_explain_func("status", 4)
seas_resource_4 <- individual_explain_func("resource", 4)

#Combining back into one dataframe
seas_separated <- seas_united |>
  left_join(seas_status_1, by = "subject") |>
  left_join(seas_resource_1, by = "subject") |>
  left_join(seas_status_2, by = "subject") |>
  left_join(seas_resource_2, by = "subject") |>
  left_join(seas_status_3, by = "subject") |>
  left_join(seas_resource_3, by = "subject") |>
  left_join(seas_status_4, by = "subject") |>
  left_join(seas_resource_4, by = "subject")
```

```{r sum-scores}
#Creating sum scores for each type of explanation
seas_separated <- seas_separated |>
  rowwise() |>
  mutate(
    ST_total = sum(c_across(matches(".*_ST_."))),
    VG_total = sum(c_across(matches(".*_VG_."))),
    SG_total = sum(c_across(matches(".*_SG_."))),
    EX_total = sum(c_across(matches(".*_EX_."))),
    IN_total = sum(c_across(matches(".*_IN_."))),
    NR_total = sum(c_across(matches(".*_NR_."))),
    MR_total = sum(c_across(matches(".*_MR_."))),
    AR_total = sum(c_across(matches(".*_AR_."))),
    EP_total = sum(c_across(matches(".*_EP_."))),
    EN_total = sum(c_across(matches(".*_EN_."))),
    PR_total = sum(c_across(matches(".*_PR_."))),
    EM_total = sum(c_across(matches(".*_EM_."))),
    MT_total = sum(c_across(matches(".*_MT_."))),
    FR_total = sum(c_across(matches(".*_FR_."))),
    PS_total = sum(c_across(matches(".*_PS_."))),
    OR_total = sum(c_across(matches(".*_OR_."))),
    ) |>
  ungroup() 
```

```{r pivot-explain}
#Pivoting explanation type
seas_pivoted <- seas_separated |>
  pivot_longer(ST_total:OR_total, names_to = "explanation_type", names_pattern = "(..)_total", values_to = "total")
```

```{r frequency-table}
#Some exploration of frequency of each type of explanation
seas_pivoted |>
  group_by(explanation_type) |>
  dplyr::summarize(
    max = max(total),
    min = min(total),
    mean = mean(total)
  )
```

# Basic Answer Categorization
## Graphs
```{r answer-col}
seas_answer_col <- seas |>
  pivot_longer(
    cols = contains("response"),
    names_to = "trial",
    values_to = "response"
  ) |>
  ggplot(aes(x = as.factor(age), fill = fct_rev(response))) +
    geom_bar(position = "fill") +
    scale_fill_manual(
      values = c(magma_colors[7], magma_colors[5], magma_colors[3]),
      labels = c("Relevant Answer", "No or Irrelevant Answer", "Missing")
      ) +
    labs(
      title = "Study 1 Explanations Given by Age",
      x = "Age (Years)",
      y = "Proportion",
      fill = NULL
    ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    legend.position = "top",
    text = element_text(family = "serif", size = 25)
        )

seas_answer_col
```

## Analyses
```{r answer-chi}
seas_response <- seas |>
  pivot_longer(
    cols = contains("response"),
    names_to = "trial",
    values_to = "response"
  )

seas_response_table <- xtabs(~response + age, data = seas_response)

seas_response_chi <- chisq.test(seas_response_table)

seas_response_chi

seas_response_posthoc <- chisq.posthoc.test(seas_response_table, method = "bonferroni")

seas_response_posthoc

seas_response_posthoc <- seas_response_posthoc |>
  rename(
    three = `3`,
    four = `4`,
    five = `5`,
    six = `6`
  )
```

A chi-square square test of independence found that there was a difference across age groups for the overall type of response participants gave to explanation questions (no or irrelevant answer, relevant answer, or missing data). Chi-squared = `r round(unname(seas_response_chi$statistic), 2)`, df = `r unname(seas_response_chi$parameter)`, p = `r signif(seas_response_chi$p.value, 2)`. 

A post-hoc test with Bonferroni correction found no differences in whether the response data was missing across age (p~3~ = `r seas_response_posthoc$three[2]`, p~4~ = `r seas_response_posthoc$four[2]`, p~5~ = `r signif(seas_response_posthoc$five[2], 2)`, p~6~ = `r seas_response_posthoc$six[2]`). There were significant differences in no/irrelevant responses and relevant responses. For no/irrelevant responses, ages 3, 5, and 6 were significant while 4 was not (p~3~ = `r seas_response_posthoc$three[4]`, p~4~ = `r seas_response_posthoc$four[4]`, p~5~ = `r signif(seas_response_posthoc$five[4], 2)`, p~6~ = `r seas_response_posthoc$six[4]`). The standardized residuals demonstrate that this difference stems from 3-year olds having a greater number of no/irrelevant responses and 5- and 6-year olds having fewer than would be expected. (residual~3~ = `r round(seas_response_posthoc$three[3], 2)`, residual~5~ = `r round(seas_response_posthoc$five[3], 2)`, residual~6~ = `r round(seas_response_posthoc$six[3], 2)`). As might be expected, relevant answers show the opposite pattern, with 6-year-olds having a greater number and 3-year-olds having a fewer number--though, note that 5-year-olds are not significant for this category (p~3~ = `r seas_response_posthoc$three[6]`, residual~3~ = `r round(seas_response_posthoc$three[5], 2)`; p~6~ = `r seas_response_posthoc$six[6]`, residual~6~ = `r round(seas_response_posthoc$six[5], 2)`).

# Number of Times a Ppt Used Explanation Across Each Response (0-8)
## Initial Graphs
```{r explain-count-basiccol}
#Column chart to see the total number of each type of explanation category participants used across their 8 explanation questions (explain better; can use multiple types of explanation in one response, but using that explanation in response will only be counted once for each question--i.e. maximum for each category is 8)
seas_pivoted |>
  ggplot(aes(x = as.factor(age), y = total, fill = explanation_type)) +
  geom_col()
```

```{r explain-count-scatter-faceted}
seas_pivoted |>
  mutate(
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")) |>
  ggplot(aes(x = age_months, y = total, color = explanation_type, fill = explanation_type)) +
  geom_jitter() +
  geom_smooth(method = "glm", alpha = 0.2) +
  facet_wrap(~explanation_type) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Study 1 Frequency of Explanation Types",
    x = "Age (Months)",
    y = "Responses to Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        )
```

## GLMMs
### Overall
```{r explain-count-lmer}
#CHECK

#Does the frequency of each answer type change with age?
seas_count_lmer <- summary(lmer(
  total ~ age_months * explanation_type + (1 | subject),
  data = seas_pivoted
)) #lmer correct? I thought it would be glmer with a poisson family but that produced errors

seas_count_lmer
```

In this model, SG (p = `r signif(seas_count_lmer$coefficients[15,5], 2)`) and SG x age (p = `r signif(seas_count_lmer$coefficients[30,5], 2)`) are significant, demonstrating that the frequencies of explanation responses (0-8 across trial) changes with these conditions.

### Exclusion
```{r EX-count-age-glm}
#Does the frequency of explanations that reference exclusion change with age?
seas_EX_count_age <- summary(glm(
  EX_total ~ age_months,
  data = seas_separated
))

seas_EX_count_age
```

The number of explanations that reference exclusion given by participants does significantly differ by age, t = `r round(seas_EX_count_age$coefficients[2,3], 2)`, p = `r signif(seas_EX_count_age$coefficients[2,4], 2)`, such that older participants are more likely to use a higher frequency of EX explanations.

```{r EX-count-QType-glm}
#Does whether a response references exclusion depend on the question type (status or resources), age, or the interaction thereof?
seas_EX_qtype <- seas_separated |>
  select(subject, age_months, matches(".*_EX_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_EX_.",
    values_to = "EX"
  )

summary(glm(
  EX ~ question_type * age_months,
  data = seas_EX_qtype
))
```

Neither question type, age, nor the interaction between the two significantly affects whether an answer references exclusion or not.

```{r EX-count-age-scatter}
EX_count_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = EX_total)) +
  geom_jitter() +
  geom_smooth(
    method = "glm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 1 Explanations Referencing Exclusion by Age",
    x = "Age (Months)",
    y = "Explanations Referencing Exclusion"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  coord_cartesian(ylim = c(0,8)) +
  scale_y_continuous(breaks = c(0, 2, 4, 8))

EX_count_age_scatter
```

### Specific Game
```{r SG-count-age-glm}
#Does the frequency of explanations that reference the game specifically change with age?
seas_SG_count_age <- summary(glm(
  SG_total ~ age_months,
  data = seas_separated
))

seas_SG_count_age
```

The number of explanations that reference the game with specific details given by participants does significantly differ by age, t = `r round(seas_SG_count_age$coefficients[2,3], 2)`, p = `r signif(seas_SG_count_age$coefficients[2,4], 2)`.

```{r SG-count-QType-glm}
#Does whether a response references the game specifically depend on the question type (status or resources), age, or the interaction thereof?
seas_SG_qtype <- seas_separated |>
  select(subject, age_months, matches(".*_SG_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_SG_.",
    values_to = "SG"
  )

summary(glm(
  SG ~ question_type * age_months,
  data = seas_SG_qtype
))
```

Whether an answer references the game specifically is significantly associated with age but not question type nor an interaction between age and question type.

```{r SG-count-age-scatter}
SG_count_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = SG_total)) +
  geom_jitter() +
  geom_smooth(
    method = "glm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 1 Explanations Referencing the Game Specifically by Age",
    x = "Age (Months)",
    y = "Explanations Referencing the Game Specifically"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )

SG_count_age_scatter
```

## Correlations
### Status
```{r explain-count-status-cor}
seas_separated <- seas_separated |> #adding status total score to this dataset
   mutate(
    status_1 = if_else(status_1 == "excluder", 1, 0),
    status_2 = if_else(status_2 == "excluder", 1, 0),
    status_3 = if_else(status_3 == "excluder", 1, 0),
    status_4 = if_else(status_4 == "excluder", 1, 0),
    status_total = status_1 + status_2 + status_3 + status_4
  )

seas_count_status_cor_data <- seas_separated |>
  select(status_total, ST_total:OR_total)

seas_count_status_cor_matrix <- rcorr(as.matrix(seas_count_status_cor_data), type = "spearman")

seas_count_status_correlation <- seas_count_status_cor_matrix$r[1, -1]
seas_count_status_p <- seas_count_status_cor_matrix$P[1, -1]

seas_count_status_df <- data.frame(rho = seas_count_status_correlation, p = seas_count_status_p)

seas_count_status_df <- seas_count_status_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas_count_status_table <- seas_count_status_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "blue") |>
    tab_header(title = "Status Total & Explanation Type Frequency Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas_count_status_table

gtsave(seas_count_status_table, "02-SEAS-Study-1-Explanatory-Analyses_files/figure-html/seas_count_status_table.png")
```

The frequencies of responses referencing Vague Game, Specific Game, Possession, and Other each displayed a significant correlation with the number of times a participant selected the excluder as being in charge. VG: rho = `r signif(unname(seas_count_status_correlation[2]), 2)` (weak negative), p = `r signif(unname(seas_count_status_p[2]), 2)`, p with Bonferroni correction = `r signif(seas_count_status_p[2] * 16, 2)`. SG: rho = `r signif(unname(seas_count_status_correlation[3]), 2)` (weak positive), p = `r signif(unname(seas_count_status_p[3]), 2)`, p with Bonferroni correction = `r signif(seas_count_status_p[3] * 16, 2)`. PS: rho = `r signif(unname(seas_count_status_correlation[15]), 2)` (weak positive), p = `r signif(unname(seas_count_status_p[15]), 2)`, p with Bonferroni correction = `r signif(seas_count_status_p[15] * 16, 2)`. OR: rho = `r signif(unname(seas_count_status_correlation[16]), 2)` (weak negative), p = `r signif(unname(seas_count_status_p[16]), 2)`, p with Bonferroni correction = `r signif(seas_count_status_p[16] * 16, 2)`. 

### Resources
```{r explain-count-resource-cor}
seas_separated <- seas_separated |> #adding resource total score to this dataset
  mutate(
    resource_1 = if_else(resource_1 == "excluder", 1, 0, NA), #One participant who did not answer the first resource question
    resource_2 = if_else(resource_2 == "excluder", 1, 0),
    resource_3 = if_else(resource_3 == "excluder", 1, 0),
    resource_4 = if_else(resource_4 == "excluder", 1, 0),
    resource_total = resource_1 + resource_2 + resource_3 + resource_4
  )

seas_count_resource_cor_data <- seas_separated |>
  select(resource_total, ST_total:OR_total)

seas_count_resource_cor_matrix <- rcorr(as.matrix(seas_count_resource_cor_data), type = "spearman")

seas_count_resource_correlation <- seas_count_resource_cor_matrix$r[1, -1]
seas_count_resource_p <- seas_count_resource_cor_matrix$P[1, -1]

seas_count_resource_df <- data.frame(rho = seas_count_resource_correlation, p = seas_count_resource_p)

seas_count_resource_df <- seas_count_resource_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas_count_resource_table <- seas_count_resource_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "pink") |>
    tab_header(title = "Resource Total & Explanation Type Frequency Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas_count_resource_table

gtsave(seas_count_resource_table, "02-SEAS-Study-1-Explanatory-Analyses_files/figure-html/seas_count_resource_table.png")
```

The frequencies of responses referencing Specific Game, Exclusion, and Possession each displayed a significant correlation with the number of times a participant selected the excluder as having more resources. SG: rho = `r signif(unname(seas_count_resource_correlation[3]), 2)` (moderate positive), p = `r signif(unname(seas_count_resource_p[3]), 2)`, p with Bonferroni correction = `r signif(seas_count_resource_p[3] * 16, 2)`. EX: rho = `r signif(unname(seas_count_resource_correlation[4]), 2)` (weak positive), p = `r signif(unname(seas_count_resource_p[4]), 2)`, p with Bonferroni correction = `r signif(seas_count_resource_p[4] * 16, 2)`. PS: rho = `r signif(unname(seas_count_resource_correlation[15]), 2)` (weak positive), p = `r signif(unname(seas_count_resource_p[15]), 2)`, p with Bonferroni correction = `r signif(seas_count_resource_p[15] * 16, 2)`.

# Did a Ppt Use Type of Explanation in Any Response?
## Initial Graphs
```{r explain-present-scatter-faceted}
seas_pivoted <- seas_pivoted |>
  mutate(
    present = if_else(total == 0, 0, 1)
  )

seas_pivoted |>
  ggplot(aes(x = age_months, y = present, color = explanation_type, fill = explanation_type)) +
  geom_point(position = position_jitter(height = .15)) +
  geom_smooth(
    method = "glm", 
    method.args = list(family = "binomial"),
    alpha = 0.2
    ) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  facet_wrap(~explanation_type) +
  labs(
    title = "Study 1 Presence of Explanation Types",
    x = "Age (Months)",
    y = "Responses Present Across Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(breaks = c(0, 1), labels = (c("Absent", "Present")))
```

## GLMMs
### Overall
```{r explain-present-lmer}
#CHECK

seas_present_lmer <- summary(lmer(
  present ~ age_months * explanation_type + (1 | subject),
  data = seas_pivoted
)) #Again, I thought this would be a binomial glmer but errors; however lmer output doesn't seem to match graphs

seas_present_lmer
```

In this model, the presence of a type of explanation across a participant's responses significantly differs based on age (p = `r signif(seas_present_lmer$coefficients[2,5], 2)`) and age x PR (p = `r signif(seas_present_lmer$coefficients[28,5], 2)`).

### Exclusion
```{r EX-present-age-glm}
#Does the presence of explanations that reference exclusion change with age?

seas_separated <- seas_separated |>
  mutate(
    across(
      .cols = ST_total:OR_total,
      .fns = ~if_else(.x > 0, 1, 0),
      .names = "{sub('total', 'present', col)}"
    )
  ) #Adding present columns to non-pivoted dataset


seas_EX_present_age <- summary(glm(
  EX_present ~ age_months,
  data = seas_separated
))

seas_EX_present_age
```

Whether participants reference exclusion at least once in the study significantly differs with age, t = `r round(seas_EX_present_age$coefficients[2,3], 2)`, p = `r signif(seas_EX_present_age$coefficients[2,4], 2)`.

```{r EX-present-age-scatter}
EX_present_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = EX_present)) +
  geom_jitter() +
  geom_smooth(
    method = "glm", 
    method.args = list(family = "binomial"), 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Explanations Referencing Exclusion by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Exclusion Referenced")
    )

EX_present_age_scatter
```

### Preferences
```{r PR-present-age-glm}
#Does the presence of explanations that reference preferences change with age?
seas_PR_present_age <- summary(glm(
  PR_present ~ age_months,
  data = seas_separated
))

seas_PR_present_age
```

Whether participants reference preferences at least once in the study does not significantly differ with age, p = `r signif(seas_PR_present_age$coefficients[2,4], 2)`.

### Specific Game
```{r SG-present-age-glm}
#Does the presence of explanations that reference the game specifically change with age?
seas_SG_present_age <- summary(glm(
  SG_present ~ age_months,
  data = seas_separated
))

seas_SG_present_age
```

Whether participants reference the game specifically at least once in the study significantly differs with age, t = `r round(seas_SG_present_age$coefficients[2,3], 2)`, p = `r signif(seas_SG_present_age$coefficients[2,4], 2)`.

```{r SG-present-age-scatter}
SG_present_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = SG_present)) +
  geom_jitter() +
  geom_smooth(
    method = "glm", 
    method.args = list(family = "binomial"),
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Explanations Referencing the Game Specifically by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Specific Game Referenced")
    )

SG_present_age_scatter
```

### Vague Game
```{r VG-present-age-glm}
#Does the presence of explanations that reference the game vaguely change with age?
seas_VG_present_age <- summary(glm(
  VG_present ~ age_months,
  data = seas_separated
))

seas_VG_present_age
```

Whether participants reference the game vaguely at least once in the study significantly differs with age, t = `r round(seas_VG_present_age$coefficients[2,3], 2)`, p = `r signif(seas_VG_present_age$coefficients[2,4], 2)`.

```{r VG-present-age-scatter}
VG_present_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = VG_present)) +
  geom_jitter() +
  geom_smooth(
    method = "glm", 
    method.args = list(family = "binomial"),
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Explanations Referencing the Game Vaguely by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Vague Game Referenced")
    )

VG_present_age_scatter
```

### Friends
```{r FR-present-age-glm}
#Does the presence of explanations that reference preferences change with age?
seas_FR_present_age <- summary(glm(
  FR_present ~ age_months,
  data = seas_separated
))

seas_FR_present_age
```

Whether participants reference friends at least once in the study significantly differs with age, t = `r round(seas_FR_present_age$coefficients[2,3], 2)`, p = `r signif(seas_FR_present_age$coefficients[2,4], 2)`.

```{r FR-present-age-scatter}
FR_present_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = FR_present)) +
  geom_jitter() +
  geom_smooth(
    method = "glm", 
    method.args = list(family = "binomial"), 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Explanations Referencing Friendship by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Friendship Referenced")
    )

FR_present_age_scatter
```

### Possessions
```{r PS-present-age-glm}
#Does the presence of explanations that reference preferences change with age?
seas_PR_present_age <- summary(glm(
  PS_present ~ age_months,
  data = seas_separated
))

seas_PR_present_age
```

Whether participants reference possessions at least once in the study significantly differs with age, t = `r round(seas_PR_present_age$coefficients[2,3], 2)`, p = `r signif(seas_PR_present_age$coefficients[2,4], 2)`.

```{r PS-present-age-scatter}
PS_present_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = PS_present)) +
  geom_jitter() +
  geom_smooth(
    method = "glm", 
    method.args = list(family = "binomial"),
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Explanations Referencing Possession by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Possession Referenced")
    )

PS_present_age_scatter
```

## Correlations
### Status
```{r explain-present-status-cor}
seas_present_status_cor_data <- seas_separated |>
  select(status_total, ST_present:OR_present)

seas_present_status_cor_matrix <- rcorr(as.matrix(seas_present_status_cor_data), type = "spearman")

seas_present_status_correlation <- seas_present_status_cor_matrix$r[1, -1]
seas_present_status_p <- seas_present_status_cor_matrix$P[1, -1]

seas_present_status_df <- data.frame(rho = seas_present_status_correlation, p = seas_present_status_p)

seas_present_status_df <- seas_present_status_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas_present_status_table <- seas_present_status_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "blue") |>
    tab_header(title = "Status Total & Explanation Type Presence Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas_present_status_table

gtsave(seas_present_status_table, "02-SEAS-Study-1-Explanatory-Analyses_files/figure-html/seas_present_status_table.png")
```

The frequencies of responses referencing Specific Game, Possession, and Other each displayed a significant correlation with the number of times a participant selected the excluder as being in charge. SG: rho = `r signif(unname(seas_present_status_correlation[3]), 2)` (weak positive), p = `r signif(unname(seas_present_status_p[3]), 2)`, p with Bonferroni correction = `r signif(seas_present_status_p[3] * 16, 2)`. PS: rho = `r signif(unname(seas_present_status_correlation[15]), 2)` (weak positive), p = `r signif(unname(seas_present_status_p[15]), 2)`, p with Bonferroni correction = `r signif(seas_present_status_p[15] * 16, 2)`. OR: rho = `r signif(unname(seas_present_status_correlation[16]), 2)` (weak negative), p = `r signif(unname(seas_present_status_p[16]), 2)`, p with Bonferroni correction = `r signif(seas_present_status_p[16] * 16, 2)`. 

### Resources
```{r explain-present-resource-cor}
seas_present_resource_cor_data <- seas_separated |>
  select(resource_total, ST_present:OR_present)

seas_present_resource_cor_matrix <- rcorr(as.matrix(seas_present_resource_cor_data), type = "spearman")

seas_present_resource_correlation <- seas_present_resource_cor_matrix$r[1, -1]
seas_present_resource_p <- seas_present_resource_cor_matrix$P[1, -1]

seas_present_resource_df <- data.frame(rho = seas_present_resource_correlation, p = seas_present_resource_p)

seas_present_resource_df <- seas_present_resource_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas_present_resource_table <- seas_present_resource_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "pink") |>
    tab_header(title = "Resource Total & Explanation Type Presence Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas_present_resource_table

gtsave(seas_present_resource_table, "02-SEAS-Study-1-Explanatory-Analyses_files/figure-html/seas_present_resource_table.png")
```

The frequencies of responses referencing Specific Game, Exclusion, and Possession each displayed a significant correlation with the number of times a participant selected the excluder as having more resources. SG: rho = `r signif(unname(seas_present_resource_correlation[3]), 2)` (moderate positive), p = `r signif(unname(seas_present_resource_p[3]), 2)`, p with Bonferroni correction = `r signif(seas_present_resource_p[3] * 16, 2)`. EX: rho = `r signif(unname(seas_present_resource_correlation[4]), 2)` (weak positive), p = `r signif(unname(seas_present_resource_p[4]), 2)`, p with Bonferroni correction = `r signif(seas_present_resource_p[4] * 16, 2)`. PS: rho = `r signif(unname(seas_present_resource_correlation[15]), 2)` (weak positive), p = `r signif(unname(seas_present_resource_p[15]), 2)`, p with Bonferroni correction = `r signif(seas_present_resource_p[15] * 16, 2)`.

# Word Count
## Graphs
```{r word-scatter}
#Scatterplot of total word count by age

seas |>
  rowwise() |>
  mutate(
    word_total = sum(c_across(contains("word"))) #could remove NAs from this step, but it's actually probably better to drop NAs from the scatter bc don't know how many words MS people would have
  ) |>
  ungroup() |>
  ggplot(aes(x = age_months, y = word_total)) +
  geom_point() +
  geom_smooth(
    method = "glm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 1 Explanation Total Word Count by Age",
    x = "Age (Months)",
    y = "Word Count"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )
```

## Analyses
```{r word-lm}
seas_wordtot <- seas |>
  rowwise() |>
  mutate(
    word_total = sum(c_across(contains("word")))) |>
  filter(!is.na(word_total))

seas_word_glm <- summary(glm(
  word_total ~ age_months,
  data = seas_wordtot
))

seas_word_glm
```

The number of words used by participants significantly differs based on age, t = `r round(seas_word_glm$coefficients[2,3], 2)`, p = `r signif(seas_word_glm$coefficients[2,4], 2)`.

