---
title: "02 SEAS Study 1 Exploratory Analyses"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Packages

```{r packages, message = FALSE, warning = FALSE}
library(readxl)
library(tidyverse)
library(lme4)
library(lmerTest)
```

# Data Preparation

```{r data-load}
seas_full <- read_excel("../Data/FINAL SEAS V1 Dataset.xlsx")

seas <- filter(seas_full, final_data == "Y") #filtering out excluded participants
```

```{r data-init-prep}
seas <- seas |>
  mutate(
    DOB = make_date(birth_year, birth_month, birth_day), #creating date of birth and date of test columns
    DOT = as_date(DOT),
    .before = DOT
  ) |>
  mutate(
    age_months = interval(DOB, DOT) %/% months(1), .after = DOT #calculating age in months
  )
```

```{r data-main-prep}
#Converting explanation data to numerical
seas_united <- seas |>
  unite("status_explain_1", status_storyref_1:status_relation_1, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_1", resource_storyref_1:resource_relation_1, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_2", status_storyref_2:status_relation_2, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_2", resource_storyref_2:resource_relation_2, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_3", status_storyref_3:status_relation_3, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_3", resource_storyref_3:resource_relation_3, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_4", status_storyref_4:status_relation_4, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_4", resource_storyref_4:resource_relation_4, sep  = " ", na.rm = TRUE)

possible_explain <- c("ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")

seas_test <- purrr::map(possible_explain, function(explain) {
    seas_united |>
      mutate(!!paste0("status_", explain, "_1") := if_else(str_detect(status_explain_1, explain), 1, 0))
  })

selected_cols <- map(seas_test, ~select(., subject, last_col()))

final_df <- reduce(selected_cols, left_join, by = "subject")



purrr::map_dfr(seas_test, ~select(., subject, last_col()))
```

```{r explain-map-func}
#Creating a general explanation mapping function
individual_explain_func <- function(status_or_resource, trial_num) {
  
  possible_explain <- c("ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")
  
  column_of_interest <- paste0(status_or_resource, "_explain_", trial_num)
  
  list_of_dfs <- purrr::map(possible_explain, function(explain) {
    seas_united |>
      mutate(!!paste0(status_or_resource, "_", explain, "_", trial_num) := if_else(str_detect(.data[[column_of_interest]], explain), 1, 0))
  })
    
    selected_cols <- map(list_of_dfs, ~select(., subject, last_col()))
    
    reduce(selected_cols, left_join, by = "subject")
  }
```

```{r explain-columns}
#Gathering individual explanation columns for each response
seas_status_1 <- individual_explain_func("status", 1)
seas_resource_1 <- individual_explain_func("resource", 1)
seas_status_2 <- individual_explain_func("status", 2)
seas_resource_2 <- individual_explain_func("resource", 2)
seas_status_3 <- individual_explain_func("status", 3)
seas_resource_3 <- individual_explain_func("resource", 3)
seas_status_4 <- individual_explain_func("status", 4)
seas_resource_4 <- individual_explain_func("resource", 4)

#Combining back into one dataframe
seas_separated <- seas_united |>
  left_join(seas_status_1, by = "subject") |>
  left_join(seas_resource_1, by = "subject") |>
  left_join(seas_status_2, by = "subject") |>
  left_join(seas_resource_2, by = "subject") |>
  left_join(seas_status_3, by = "subject") |>
  left_join(seas_resource_3, by = "subject") |>
  left_join(seas_status_4, by = "subject") |>
  left_join(seas_resource_4, by = "subject")
```

```{r sum-scores}
seas_separated <- seas_separated |>
  rowwise() |>
  mutate(
    ST_total = sum(c_across(matches(".*_ST_."))),
    VG_total = sum(c_across(matches(".*_VG_."))),
    SG_total = sum(c_across(matches(".*_SG_."))),
    EX_total = sum(c_across(matches(".*_EX_."))),
    IN_total = sum(c_across(matches(".*_IN_."))),
    NR_total = sum(c_across(matches(".*_NR_."))),
    MR_total = sum(c_across(matches(".*_MR_."))),
    AR_total = sum(c_across(matches(".*_AR_."))),
    EP_total = sum(c_across(matches(".*_EP_."))),
    EN_total = sum(c_across(matches(".*_EN_."))),
    PR_total = sum(c_across(matches(".*_PR_."))),
    EM_total = sum(c_across(matches(".*_EM_."))),
    MT_total = sum(c_across(matches(".*_MT_."))),
    FR_total = sum(c_across(matches(".*_FR_."))),
    PS_total = sum(c_across(matches(".*_PS_."))),
    OR_total = sum(c_across(matches(".*_OR_."))),
    ) |>
  ungroup() 
```

```{r pivot-explain}
#Pivoting explanation type
seas_pivoted <- seas_separated |>
  pivot_longer(ST_total:OR_total, names_to = "explanation_type", names_pattern = "(..)_total", values_to = "total")
```

```{r}
#some exploration of frequency of each type of explanation

seas_pivoted |>
  group_by(explanation_type) |>
  summarize(
    max = max(total),
    min = min(total),
    mean = mean(total)
  )
```

# Basic Answer Categorization

## Graphs
```{r answer-col}
seas |>
  pivot_longer(
    cols = contains("response"),
    names_to = "trial",
    values_to = "response"
  ) |>
#  group_by(response) |>
#  summarize(n = n())
  
  ggplot(aes(x = as.factor(age), fill = fct_rev(response))) +
    geom_bar(position = "fill") +
    scale_fill_manual(
      values = c(magma_colors[7], magma_colors[5], magma_colors[3]),
      labels = c("Relevant Answer", "No or Irrelevant Answer", "Missing")
      ) +
    labs(
      title = "Explanations Given by Age",
      x = "Age (Years)",
      y = "Proportion",
      fill = NULL
    ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    legend.position = "top",
    text = element_text(family = "serif", size = 25)
        )
```

## Analyses
```{r answer-chi}
seas_response_contingency <- seas |>
  pivot_longer(
    cols = contains("response"),
    names_to = "trial",
    values_to = "response"
  ) |>
  count(response, age) |>
  pivot_wider(
    names_from = age, values_from = n, values_fill = 0L
  ) |>
  select(-response) |>
  as.matrix()

seas_response_chi <- chisq.test(seas_response_contingency)

seas_response_chi
```

Significant. What post-hoc test should we use?

# Number of Times a Ppt Used Explanation Across Each Response (0-8)

## Graphs
```{r explain-count-basiccol}
#column chart to see the total number of each type of explanation category participants used across their 8 explanation questions (explain better; can use multiple types of explanation in one response, but using that explanation in response will only be counted once for each question--i.e. maximum for each category is 8)

seas_pivoted |>
  ggplot(aes(x = as.factor(age), y = total, fill = explanation_type)) +
  geom_col()
```

```{r explain-count-scatter}
#Scatterplot of explanation types across age
wo_black <- viridis::magma(20)[5:20]

seas_pivoted |>
  mutate(
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")) |>
  ggplot(aes(x = age_months, y = total, color = explanation_type, fill = explanation_type)) +
  geom_jitter() +
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Types of Explanations in All Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses to Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        )
```

```{r explain-count-scatter-faceted}
seas_pivoted |>
  mutate(
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")) |>
  ggplot(aes(x = age_months, y = total, color = explanation_type, fill = explanation_type)) +
  geom_jitter() +
  geom_smooth(method = "lm", alpha = 0.2) +
  facet_wrap(~explanation_type) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Types of Explanations in All Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses to Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        )
```

## Analyses

```{r explain-count-lm}
summary(lmer(
  total ~ age_months + (1 | subject),
  data = seas_pivoted
))

summary(lmer(
  total ~ age_months * explanation_type + (1 | subject),
  data = seas_pivoted
))
```

Age alone: age significant

Combination: SG, ST, age x SG significant; age x VG significant

# Did a Ppt Use Type of Explanation in Any Response?

## Graphs

```{r explain-present-scatter}
seas_pivoted <- seas_pivoted |>
  mutate(
    present = if_else(total == 0, 0, 1), 
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")
  )

seas_pivoted|>
  ggplot(aes(x = age_months, y = present, color = explanation_type, fill = explanation_type)) +
  geom_point(position = position_jitter(height = .15)) +
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Types of Explanations Present in Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses Present Across Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(breaks = c(0, 1), labels = (c("Absent", "Present")))
```

```{r explain-present-scatter-faceted}
seas_pivoted |>
  ggplot(aes(x = age_months, y = present, color = explanation_type, fill = explanation_type)) +
  geom_point(position = position_jitter(height = .15)) +
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  facet_wrap(~explanation_type) +
  labs(
    title = "Types of Explanations Present in Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses Present Across Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(breaks = c(0, 1), labels = (c("Absent", "Present")))
```

## Analyses

```{r explain-present-lm}
#or is glmer correct here?

summary(lmer(
  present ~ age_months + (1 | subject),
  data = seas_pivoted
))

summary(lmer(
  present ~ age_months * explanation_type + (1 | subject),
  data = seas_pivoted
))
```

Age alone: significant

Combination: EX, age x EM, age x MT significant

# Word Count

## Graphs

```{r word-scatter}
#Scatterplot of total word count by age

seas |>
  rowwise() |>
  mutate(
    word_total = sum(c_across(contains("word"))) #could remove NAs from this step, but it's actually probably better to drop NAs from the scatter bc don't know how many words MS people would have
  ) |>
  ungroup() |>
  ggplot(aes(x = age_months, y = word_total)) +
  geom_point() +
  stat_smooth(method = "lm", formula = y ~ x)

```

## Analyses

```{r word-lm}
#not working lol

seas_wordtot <- seas |>
  rowwise() |>
  mutate(
    word_total = sum(c_across(contains("word")))) |>
  filter(!is.na(word_total))

summary(lmer(
  word_total ~ age_months + (1 | subject),
  data = seas_wordtot
))
```

## also add NA/RA/MS

```{r mapping-function-test, eval = FALSE, echo = FALSE}
status_or_resource <- "status"
trial_num <- 1

possible_explain <- c("ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")
  
  column_of_interest <- paste0(status_or_resource, "_explain_", trial_num)
  
  list_of_dfs <- purrr::map(possible_explain, function(explain) {
    seas_united |>
      mutate(!!paste0(status_or_resource, "_", explain, "_", trial_num) := if_else(str_detect(.data[[column_of_interest]], explain), 1, 0)) 
  })
    
    selected_cols <- map(list_of_dfs, ~select(., subject, last_col()))
    
    View(reduce(selected_cols, left_join, by = "subject"))
```

```{r mapping-test, eval = FALSE, echo = FALSE}
possible_explain <- c("ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")

seas_test <- purrr::map(possible_explain, function(explain) {
    seas_united |>
      mutate(!!paste0("status_", explain, "_1") := if_else(str_detect(status_explain_1, explain), 1, 0))
  })

selected_cols <- map(seas_test, ~select(., subject, last_col()))

final_df <- reduce(selected_cols, left_join, by = "subject")



purrr::map_dfr(seas_test, ~select(., subject, last_col()))
```
