---
title: "02 SEAS Study 1 Exploratory Analyses"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Packages
```{r packages, message = FALSE, warning = FALSE}
library(readxl)
library(tidyverse)
library(lme4)
library(lmerTest)
library(showtext)
library(viridis)

showtext_auto()
```

# Data Preparation
```{r data-colors}
magma_colors <- c("#000004FF", "#180F3EFF", "#451077FF", "#721F81FF", "#9F2F7FFF", "#CD4071FF", "#F1605DFF", "#FD9567FF", "#FEC98DFF", "#FCFDBFFF") #from magma(10)
```

```{r data-load}
seas_full <- read_excel("../Data/FINAL SEAS V1 Dataset.xlsx")

seas <- filter(seas_full, final_data == "Y") #filtering out excluded participants
```

```{r data-init-prep}
seas <- seas |>
  mutate(
    DOB = make_date(birth_year, birth_month, birth_day), #creating date of birth and date of test columns
    DOT = as_date(DOT),
    .before = DOT
  ) |>
  mutate(
    age_months = interval(DOB, DOT) %/% months(1), .after = DOT #calculating age in months
  )
```

```{r data-main-prep}
#Combining any explanation code for a particular response
seas_united <- seas |>
  unite("status_explain_1", status_storyref_1:status_relation_1, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_1", resource_storyref_1:resource_relation_1, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_2", status_storyref_2:status_relation_2, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_2", resource_storyref_2:resource_relation_2, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_3", status_storyref_3:status_relation_3, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_3", resource_storyref_3:resource_relation_3, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_4", status_storyref_4:status_relation_4, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_4", resource_storyref_4:resource_relation_4, sep  = " ", na.rm = TRUE)
```

```{r explain-map-func}
#Creating a general explanation mapping function
individual_explain_func <- function(status_or_resource, trial_num) {
  
  possible_explain <- c("ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")
  
  column_of_interest <- paste0(status_or_resource, "_explain_", trial_num)
  
  list_of_dfs <- purrr::map(possible_explain, function(explain) {
    seas_united |>
      mutate(!!paste0(status_or_resource, "_", explain, "_", trial_num) := if_else(str_detect(.data[[column_of_interest]], explain), 1, 0))
  })
    
    selected_cols <- map(list_of_dfs, ~select(., subject, last_col()))
    
    reduce(selected_cols, left_join, by = "subject")
  }
```

```{r explain-columns}
#Gathering individual explanation columns for each response
seas_status_1 <- individual_explain_func("status", 1)
seas_resource_1 <- individual_explain_func("resource", 1)
seas_status_2 <- individual_explain_func("status", 2)
seas_resource_2 <- individual_explain_func("resource", 2)
seas_status_3 <- individual_explain_func("status", 3)
seas_resource_3 <- individual_explain_func("resource", 3)
seas_status_4 <- individual_explain_func("status", 4)
seas_resource_4 <- individual_explain_func("resource", 4)

#Combining back into one dataframe
seas_separated <- seas_united |>
  left_join(seas_status_1, by = "subject") |>
  left_join(seas_resource_1, by = "subject") |>
  left_join(seas_status_2, by = "subject") |>
  left_join(seas_resource_2, by = "subject") |>
  left_join(seas_status_3, by = "subject") |>
  left_join(seas_resource_3, by = "subject") |>
  left_join(seas_status_4, by = "subject") |>
  left_join(seas_resource_4, by = "subject")
```

```{r sum-scores}
#Creating sum scores for each type of explanation
seas_separated <- seas_separated |>
  rowwise() |>
  mutate(
    ST_total = sum(c_across(matches(".*_ST_."))),
    VG_total = sum(c_across(matches(".*_VG_."))),
    SG_total = sum(c_across(matches(".*_SG_."))),
    EX_total = sum(c_across(matches(".*_EX_."))),
    IN_total = sum(c_across(matches(".*_IN_."))),
    NR_total = sum(c_across(matches(".*_NR_."))),
    MR_total = sum(c_across(matches(".*_MR_."))),
    AR_total = sum(c_across(matches(".*_AR_."))),
    EP_total = sum(c_across(matches(".*_EP_."))),
    EN_total = sum(c_across(matches(".*_EN_."))),
    PR_total = sum(c_across(matches(".*_PR_."))),
    EM_total = sum(c_across(matches(".*_EM_."))),
    MT_total = sum(c_across(matches(".*_MT_."))),
    FR_total = sum(c_across(matches(".*_FR_."))),
    PS_total = sum(c_across(matches(".*_PS_."))),
    OR_total = sum(c_across(matches(".*_OR_."))),
    ) |>
  ungroup() 
```

```{r pivot-explain}
#Pivoting explanation type
seas_pivoted <- seas_separated |>
  pivot_longer(ST_total:OR_total, names_to = "explanation_type", names_pattern = "(..)_total", values_to = "total")
```

```{r frequency-table}
#some exploration of frequency of each type of explanation
seas_pivoted |>
  group_by(explanation_type) |>
  summarize(
    max = max(total),
    min = min(total),
    mean = mean(total)
  )
```

# Basic Answer Categorization

## Graphs
```{r answer-col}
seas |>
  pivot_longer(
    cols = contains("response"),
    names_to = "trial",
    values_to = "response"
  ) |>
  ggplot(aes(x = as.factor(age), fill = fct_rev(response))) +
    geom_bar(position = "fill") +
    scale_fill_manual(
      values = c(magma_colors[7], magma_colors[5], magma_colors[3]),
      labels = c("Relevant Answer", "No or Irrelevant Answer", "Missing")
      ) +
    labs(
      title = "Study 1 Explanations Given by Age",
      x = "Age (Years)",
      y = "Proportion",
      fill = NULL
    ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    legend.position = "top",
    text = element_text(family = "serif", size = 25)
        )
```

## Analyses
```{r answer-chi}
seas_response_contingency <- seas |>
  pivot_longer(
    cols = contains("response"),
    names_to = "trial",
    values_to = "response"
  ) |>
  count(response, age) |>
  pivot_wider(
    names_from = age, values_from = n, values_fill = 0L
  ) |>
  select(-response) |>
  as.matrix()

seas_response_chi <- chisq.test(seas_response_contingency)

seas_response_chi
```

Significant. What post-hoc test should we use?

# Number of Times a Ppt Used Explanation Across Each Response (0-8)

## Initial Graphs
```{r explain-count-basiccol}
#column chart to see the total number of each type of explanation category participants used across their 8 explanation questions (explain better; can use multiple types of explanation in one response, but using that explanation in response will only be counted once for each question--i.e. maximum for each category is 8)

seas_pivoted |>
  ggplot(aes(x = as.factor(age), y = total, fill = explanation_type)) +
  geom_col()
```

```{r explain-count-scatter}
#Scatterplot of explanation types across age
wo_black <- viridis::magma(20)[5:20]

seas_pivoted |>
  mutate(
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")) |>
  ggplot(aes(x = age_months, y = total, color = explanation_type, fill = explanation_type)) +
  geom_jitter() +
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Types of Explanations in All Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses to Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        )
```

```{r explain-count-scatter-faceted}
seas_pivoted |>
  mutate(
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")) |>
  ggplot(aes(x = age_months, y = total, color = explanation_type, fill = explanation_type)) +
  geom_jitter() +
  geom_smooth(method = "lm", alpha = 0.2) +
  facet_wrap(~explanation_type) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Types of Explanations in All Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses to Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        )
```

## Analyses

### Overall
```{r explain-count-lmer}
#Does the frequency of each answer type change with age?
summary(lmer(
  total ~ age_months * explanation_type + (1 | subject),
  data = seas_pivoted
)) #lmer correct? I thought it would be glmer with a poisson family but that produced errors
```

In this model, SG and SG x age are significant, demonstrating that the frequencies of explanation responses (0-8 across trial) changes with these conditons.

### Exclusion
```{r EX-count-age-glm}
#Does the frequency of explanations that reference exclusion change with age?
summary(glm(
  EX_total ~ age_months,
  data = seas_separated
))
```

The number of explanations that reference exclusion given by participants does significantly differ by age.

```{r EX-count-QType-glm}
#does whether a response references exclusion depend on the question type (status or resources), age, or the interaction thereof?
seas_EX_qtype <- seas_separated |>
  select(subject, age_months, matches(".*_EX_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_EX_.",
    values_to = "EX"
  )

summary(glm(
  EX ~ question_type * age_months,
  data = seas_EX_qtype
))
```

Neither question type, age, nor the interaction between the two significantly affects whether an answer references exclusion or not.

### Specific Game
```{r SG-count-age-glm}
#Does the frequency of explanations that reference the game specifically change with age?
summary(glm(
  SG_total ~ age_months,
  data = seas_separated
))
```

The number of explanations that reference the game with specific details given by participants does significantly differ by age.

```{r SG-count-QType-glm}
#does whether a response references the game specifically depend on the question type (status or resources), age, or the interaction thereof?
seas_SG_qtype <- seas_separated |>
  select(subject, age_months, matches(".*_SG_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_SG_.",
    values_to = "SG"
  )

summary(glm(
  SG ~ question_type * age_months,
  data = seas_SG_qtype
))
```

Whether an answer references the game specifically is significantly associated with age but not question type nor an interaction between age and question type.

## Follow-Up Graphs
```{r EX-count-age-scatter}
EX_count_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = EX_total)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 1 Explanations Referencing Exclusion by Age",
    x = "Age (Months)",
    y = "Explanations Referencing Exclusion"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )

EX_count_age_scatter
#Also the actual possible range of responses is 0-8, so this graph would look even worse zoomed out
```

```{r SG-count-age-scatter}
SG_count_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = SG_total)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 1 Explanations Referencing the Game Specifically by Age",
    x = "Age (Months)",
    y = "Explanations Referencing the Game Specifically"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )

SG_count_age_scatter
```

# Did a Ppt Use Type of Explanation in Any Response?

## Initial Graphs
```{r explain-present-scatter}
seas_pivoted <- seas_pivoted |>
  mutate(
    present = if_else(total == 0, 0, 1), 
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")
  )

seas_pivoted|>
  ggplot(aes(x = age_months, y = present, color = explanation_type, fill = explanation_type)) +
  geom_point(position = position_jitter(height = .15)) +
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Types of Explanations Present in Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses Present Across Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(breaks = c(0, 1), labels = (c("Absent", "Present")))
```

```{r explain-present-scatter-faceted}
seas_pivoted |>
  ggplot(aes(x = age_months, y = present, color = explanation_type, fill = explanation_type)) +
  geom_point(position = position_jitter(height = .15)) +
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  facet_wrap(~explanation_type) +
  labs(
    title = "Study 1 Types of Explanations Present in Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses Present Across Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(breaks = c(0, 1), labels = (c("Absent", "Present")))
```

## Analyses

### Overall
```{r explain-present-lmer}
summary(lmer(
  present ~ age_months * explanation_type + (1 | subject),
  data = seas_pivoted
)) #Again, I thought this would be a binomial glmer but errors; however lmer output doesn't seem to match graphs
```

In this model, the presence of a type of explanation across a participant's responses significantly differs based on age, age x PR, and age x MT.

### Exclusion
```{r EX-present-age-glm}
#Does the presence of explanations that reference exclusion change with age?

seas_separated <- seas_separated |>
  mutate(
    across(
      .cols = ST_total:OR_total,
      .fns = ~if_else(.x > 0, 1, 0),
      .names = "{sub('total', 'present', col)}"
    )
  ) #Adding present columns to non-pivoted dataset


summary(glm(
  EX_present ~ age_months,
  data = seas_separated
))
```

Whether participants reference exclusion at least once in the study significantly differs with age.

### Preferences
```{r PR-present-age-glm}
#Does the presence of explanations that reference preferences change with age?
summary(glm(
  PR_present ~ age_months,
  data = seas_separated
))
```

Whether participants reference preferences at least once in the study does not significantly differ with age.

### Motivation
```{r MT-present-age-glm}
#Does the presence of explanations that reference motivations change with age?
summary(glm(
  MT_present ~ age_months,
  data = seas_separated
))
```

Whether participants reference motivations at least once in the study does not significantly differ with age.

### Specific Game
```{r SG-present-age-glm}
#Does the presence of explanations that reference the game specifically change with age?
summary(glm(
  SG_present ~ age_months,
  data = seas_separated
))
```

Whether participants reference the game specifically at least once in the study significantly differs with age.

### Vague Game
```{r VG-present-age-glm}
#Does the presence of explanations that reference the game vaguely change with age?
summary(glm(
  VG_present ~ age_months,
  data = seas_separated
))
```

Whether participants reference the game vaguely at least once in the study significantly differs with age.

### Friends
```{r FR-present-age-glm}
#Does the presence of explanations that reference preferences change with age?
summary(glm(
  FR_present ~ age_months,
  data = seas_separated
))
```

Whether participants reference friends at least once in the study significantly differs with age.

### Possessions
```{r PS-present-age-glm}
#Does the presence of explanations that reference preferences change with age?
summary(glm(
  PS_present ~ age_months,
  data = seas_separated
))
```

Whether participants reference possessions at least once in the study significantly differs with age.

## Follow-Up Graphs
```{r EX-presence-age-scatter}
EX_presence_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = EX_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Explanations Referencing Exclusion by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Exclusion Referenced")
    )

EX_presence_age_scatter
```

```{r SG-presence-age-scatter}
SG_presence_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = SG_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Explanations Referencing the Game Specifically by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Specific Game Referenced")
    )

SG_presence_age_scatter
```

```{r VG-presence-age-scatter}
VG_presence_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = VG_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Explanations Referencing the Game Vaguely by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Vague Game Referenced")
    )

VG_presence_age_scatter
```

```{r FR-presence-age-scatter}
FR_presence_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = FR_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Explanations Referencing Friendship by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Friendship Referenced")
    )

FR_presence_age_scatter
```

```{r PS-presence-age-scatter}
PS_presence_age_scatter <- seas_separated |>
  ggplot(aes(x = age_months, y = PS_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 1 Explanations Referencing Possession by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Possession Referenced")
    )

PS_presence_age_scatter
```

# Word Count

## Graphs
```{r word-scatter}
#Scatterplot of total word count by age

seas |>
  rowwise() |>
  mutate(
    word_total = sum(c_across(contains("word"))) #could remove NAs from this step, but it's actually probably better to drop NAs from the scatter bc don't know how many words MS people would have
  ) |>
  ungroup() |>
  ggplot(aes(x = age_months, y = word_total)) +
  geom_point() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 1 Explanation Total Word Count by Age",
    x = "Age (Months)",
    y = "Word Count"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )
```

## Analyses
```{r word-lm, error = TRUE}
seas_wordtot <- seas |>
  rowwise() |>
  mutate(
    word_total = sum(c_across(contains("word")))) |>
  filter(!is.na(word_total))

summary(glm(
  word_total ~ age_months,
  data = seas_wordtot
))
```

The number of words used by participants significantly differs based on age.
