---
title: "04 SEAS Study 2 Exploratory Analyses"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

# Packages

```{r packages, message = FALSE, warning = FALSE}
library(readxl)
library(tidyverse)
library(lme4)
library(lmerTest)
library(showtext)
library(viridis)
library(chisq.posthoc.test)

showtext_auto()
```

# Data Preparation

```{r data-colors}
magma_colors <- c("#000004FF", "#180F3EFF", "#451077FF", "#721F81FF", "#9F2F7FFF", "#CD4071FF", "#F1605DFF", "#FD9567FF", "#FEC98DFF", "#FCFDBFFF") #from magma(10)
```

```{r data-load}
seas2_full <- read_excel("../Data/FINAL SEAS V2 Dataset.xlsx")

seas2 <- subset(seas2_full, final_data == "Y") # dropping excluded participants
```

```{r data-init-prep}
seas2 <- seas2 |>
  mutate(
    DOB = make_date(birth_year, birth_month, birth_day), #creating date of birth and date of test columns
    DOT = as_date(DOT),
    .before = DOT
  ) |>
  mutate(
    age_months = interval(DOB, DOT) %/% months(1), .after = DOT #calculating age in months
  )
```

```{r data-main-prep}
#Combining any explanation code for a particular response
seas2_united <- seas2 |>
  unite("status_explain_1", status_storyref_1:status_relation_1, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_1", resource_storyref_1:resource_relation_1, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_2", status_storyref_2:status_relation_2, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_2", resource_storyref_2:resource_relation_2, sep  = " ", na.rm = TRUE) |>
   unite("status_explain_comp1", comp_status_storyref_1:comp_status_relation_1, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_comp1", comp_resource_storyref_1:comp_resource_relation_1, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_3", status_storyref_3:status_relation_3, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_3", resource_storyref_3:resource_relation_3, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_4", status_storyref_4:status_relation_4, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_4", resource_storyref_4:resource_relation_4, sep  = " ", na.rm = TRUE) |>
unite("status_explain_comp2", comp_status_storyref_2:comp_status_relation_2, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_comp2", comp_resource_storyref_2:comp_resource_relation_2, sep  = " ", na.rm = TRUE)
```

```{r explain-map-func}
#Creating a general explanation mapping function
individual_explain_func <- function(status_or_resource, trial_num) {
  
  possible_explain <- c("ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")
  
  column_of_interest <- paste0(status_or_resource, "_explain_", trial_num)
  
  list_of_dfs <- purrr::map(possible_explain, function(explain) {
    seas2_united |>
      mutate(!!paste0(status_or_resource, "_", explain, "_", trial_num) := if_else(str_detect(.data[[column_of_interest]], explain), 1, 0))
  })
    
    selected_cols <- map(list_of_dfs, ~select(., subject, last_col()))
    
    reduce(selected_cols, left_join, by = "subject")
  }
```

```{r explain-columns}
#Gathering individual explanation columns for each response
seas2_status_1 <- individual_explain_func("status", 1)
seas2_resource_1 <- individual_explain_func("resource", 1)
seas2_status_2 <- individual_explain_func("status", 2)
seas2_resource_2 <- individual_explain_func("resource", 2)
seas2_status_comp1 <- individual_explain_func("status", "comp1")
seas2_resource_comp1 <- individual_explain_func("resource", "comp1")
seas2_status_3 <- individual_explain_func("status", 3)
seas2_resource_3 <- individual_explain_func("resource", 3)
seas2_status_4 <- individual_explain_func("status", 4)
seas2_resource_4 <- individual_explain_func("resource", 4)
seas2_status_comp2 <- individual_explain_func("status", "comp2")
seas2_resource_comp2 <- individual_explain_func("resource", "comp2")

#Combining back into one dataframe
seas2_separated <- seas2_united |>
  left_join(seas2_status_1, by = "subject") |>
  left_join(seas2_resource_1, by = "subject") |>
  left_join(seas2_status_2, by = "subject") |>
  left_join(seas2_resource_2, by = "subject") |>
  left_join(seas2_status_comp1, by = "subject") |>
  left_join(seas2_resource_comp1, by = "subject") |>
  left_join(seas2_status_3, by = "subject") |>
  left_join(seas2_resource_3, by = "subject") |>
  left_join(seas2_status_4, by = "subject") |>
  left_join(seas2_resource_4, by = "subject") |>
  left_join(seas2_status_comp2, by = "subject") |>
  left_join(seas2_resource_comp2, by = "subject")
```

```{r sum-scores}
#Creating sum scores for each type of explanation
seas2_separated <- seas2_separated |>
  rowwise() |>
  mutate(
    ST_total = sum(c_across(matches(".*_ST_."))),
    VG_total = sum(c_across(matches(".*_VG_."))),
    SG_total = sum(c_across(matches(".*_SG_."))),
    EX_total = sum(c_across(matches(".*_EX_."))),
    IN_total = sum(c_across(matches(".*_IN_."))),
    NR_total = sum(c_across(matches(".*_NR_."))),
    MR_total = sum(c_across(matches(".*_MR_."))),
    AR_total = sum(c_across(matches(".*_AR_."))),
    EP_total = sum(c_across(matches(".*_EP_."))),
    EN_total = sum(c_across(matches(".*_EN_."))),
    PR_total = sum(c_across(matches(".*_PR_."))),
    EM_total = sum(c_across(matches(".*_EM_."))),
    MT_total = sum(c_across(matches(".*_MT_."))),
    FR_total = sum(c_across(matches(".*_FR_."))),
    PS_total = sum(c_across(matches(".*_PS_."))),
    OR_total = sum(c_across(matches(".*_OR_."))),
    ) |>
  ungroup() 
```

```{r pivot-explain}
#Pivoting explanation type
seas2_pivoted <- seas2_separated |>
  pivot_longer(ST_total:OR_total, names_to = "explanation_type", names_pattern = "(..)_total", values_to = "total")
```

```{r frequency-table}
#some exploration of frequency of each type of explanation
seas2_pivoted |>
  group_by(explanation_type) |>
  summarize(
    max = max(total),
    min = min(total),
    mean = mean(total)
  )
```

# Basic Answer Categorization

## Graphs

```{r answer-col}
seas2 |>
  pivot_longer(
    cols = contains("response"),
    names_to = "trial",
    values_to = "response"
  ) |>
  ggplot(aes(x = as.factor(age), fill = fct_rev(response))) +
    geom_bar(position = "fill") +
    scale_fill_manual(
      values = c(magma_colors[7], magma_colors[5], magma_colors[3]),
      labels = c("Relevant Answer", "No or Irrelevant Answer", "Missing")
      ) +
    labs(
      title = "Study 2 Explanations Given by Age",
      x = "Age (Years)",
      y = "Proportion",
      fill = NULL
    ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    legend.position = "top",
    text = element_text(family = "serif", size = 25)
        )
```

## Analyses

```{r answer-chi}
seas2_response <- seas2 |>
  pivot_longer(
    cols = contains("response"),
    names_to = "trial",
    values_to = "response"
  )

seas2_response_table <- xtabs(~response + age, data = seas2_response)

seas2_response_chi <- chisq.test(seas2_response_table)

seas2_response_chi

seas2_response_posthoc <- chisq.posthoc.test(seas2_response_table, method = "bonferroni")

seas2_response_posthoc

seas2_response_posthoc <- seas2_response_posthoc |>
  rename(
    three = `3`,
    four = `4`,
    five = `5`,
    six = `6`
  )
```

A chi-square square test of independence found that there was a difference across age groups for the overall type of response participants gave to explanation questions (no or irrelevant answer, relevant answer, or missing data). Chi-squared = `r round(unname(seas2_response_chi$statistic), 2)`, df = `r unname(seas2_response_chi$parameter)`, p = `r signif(seas2_response_chi$p.value, 2)`.

A post-hoc test with Bonferroni correction found one significant difference in whether the response data was missing across age (p~3~ = `r seas2_response_posthoc$three[2]`, p~4~ = `r seas2_response_posthoc$four[2]`, p~5~ = `r signif(seas2_response_posthoc$five[2], 2)`, p~6~ = `r seas2_response_posthoc$six[2]`), with 5-year-olds having fewer missing responses than would be expected (adjusted residual = `r round(seas2_response_posthoc$five[1])`), likely due to the fact that there are no missing responses among this age group. 

Additionally, there were significant differences in no/irrelevant responses and relevant responses. For no/irrelevant responses, ages 3 and 6 were significant while 4 and 5 were not (p~3~ = `r seas2_response_posthoc$three[4]`, p~4~ = `r seas2_response_posthoc$four[4]`, p~5~ = `r signif(seas2_response_posthoc$five[4], 2)`, p~6~ = `r seas2_response_posthoc$six[4]`). The standardized residuals demonstrate that this difference stems from 3-year olds having a greater number of no/irrelevant responses and 6-year olds having fewer than would be expected. (residual~3~ = `r round(seas2_response_posthoc$three[3], 2)`, residual~6~ = `r round(seas2_response_posthoc$six[3], 2)`). A slightly different pattern is found for relevant answers, with 3- and 5-year-old being the only significant groups, such that 5-year-olds have a greater number and 3-year-olds fewer  (p~3~ = `r seas2_response_posthoc$three[6]`, residual~3~ = `r round(seas2_response_posthoc$three[5], 2)`; p~5~ = `r seas2_response_posthoc$five[6]`, residual~5~ = `r round(seas2_response_posthoc$five[5], 2)`).

# Number of Times a Ppt Used Explanation Across Each Response (0-8)

## Initial Graphs

```{r explain-count-basiccol}
#column chart to see the total number of each type of explanation category participants used across their 8 explanation questions (explain better; can use multiple types of explanation in one response, but using that explanation in response will only be counted once for each question--i.e. maximum for each category is 8)

seas2_pivoted |>
  ggplot(aes(x = as.factor(age), y = total, fill = explanation_type)) +
  geom_col()
```

```{r explain-count-scatter}
#Scatterplot of explanation types across age
wo_black <- viridis::magma(20)[5:20]

seas2_pivoted |>
  mutate(
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")) |>
  ggplot(aes(x = age_months, y = total, color = explanation_type, fill = explanation_type)) +
  geom_jitter() +
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Types of Explanations in All Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses to Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        )
```

```{r explain-count-scatter-faceted}
seas2_pivoted |>
  mutate(
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")) |>
  ggplot(aes(x = age_months, y = total, color = explanation_type, fill = explanation_type)) +
  geom_jitter() +
  geom_smooth(method = "lm", alpha = 0.2) +
  facet_wrap(~explanation_type) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Types of Explanations in All Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses to Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        )
```

## Analyses

### Overall

```{r explain-count-lmer}
#Does the frequency of each answer type change with age?
summary(lmer(
  total ~ age_months * explanation_type + (1 | subject),
  data = seas2_pivoted
)) #lmer correct? I thought it would be glmer with a poisson family but that produced errors
```

In this model,  SG x age and ST x age are significant, demonstrating that the frequencies of explanation responses (0-12 across trial) changes with these conditions.

### Exclusion

```{r EX-count-age-glm}
#Does the frequency of explanations that reference exclusion change with age?
summary(glm(
  EX_total ~ age_months,
  data = seas2_separated
))
```

The number of explanations that reference exclusion given by participants does significantly differ by age.

```{r EX-count-QType-glm}
#does whether a response references exclusion depend on the question type (status or resources), age, or the interaction thereof?
seas2_EX_qtype <- seas2_separated |>
  select(subject, age_months, matches(".*_EX_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_EX_.",
    values_to = "EX"
  )

summary(glm(
  EX ~ question_type * age_months,
  data = seas2_EX_qtype
))
```

According to this model, the number of explanations that reference exclusion differs based on age, but not based on the type of question (status vs resources) or an interaction between the two.

### Inclusion

```{r IN-count-age-glm}
#Does the frequency of explanations that reference exclusion change with age?
summary(glm(
  IN_total ~ age_months,
  data = seas2_separated
))
```

The number of explanations that reference inclusion given by participants does significantly differ by age.

```{r IN-count-QType-glm}
#does whether a response references inclusion depend on the question type (status or resources), age, or the interaction thereof?
seas2_IN_qtype <- seas2_separated |>
  select(subject, age_months, matches(".*_IN_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_IN_.",
    values_to = "IN"
  )

summary(glm(
  IN ~ question_type * age_months,
  data = seas2_IN_qtype
))
```

According to this model, the number of explanations that reference inclusion differs based on age, but not based on the type of question (status vs resources) or an interaction between the two.

### Specific Game

```{r SG-count-age-glm}
#Does the frequency of explanations that reference the game specifically change with age?
summary(glm(
  SG_total ~ age_months,
  data = seas2_separated
))
```

The number of explanations that reference the game with specific details given by participants does significantly differ by age.

```{r SG-count-QType-glm}
#does whether a response references the game specifically depend on the question type (status or resources), age, or the interaction thereof?
seas2_SG_qtype <- seas2_separated |>
  select(subject, age_months, matches(".*_SG_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_SG_.",
    values_to = "SG"
  )

summary(glm(
  SG ~ question_type * age_months,
  data = seas2_SG_qtype
))
```

Whether an answer references the game specifically is significantly associated with age but not question type nor an interaction between age and question type.

### Superficial Traits

```{r ST-count-age-glm}
#Does the frequency of explanations that reference the game specifically change with age?
summary(glm(
  ST_total ~ age_months,
  data = seas2_separated
))
```

The number of explanations that reference superficial traits about a character given by participants does not significantly differ by age.

```{r ST-count-QType-glm}
#does whether a response references the game specifically depend on the question type (status or resources), age, or the interaction thereof?
seas2_ST_qtype <- seas2_separated |>
  select(subject, age_months, matches(".*_ST_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_ST_.",
    values_to = "ST"
  )

summary(glm(
  ST ~ question_type * age_months,
  data = seas2_ST_qtype
))
```

Whether an answer references a character's superficial traits is not significantly associated with age, question type, or an interaction between the two.

## Follow-Up Graphs

```{r EX-count-age-scatter}
EX_count_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = EX_total)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 2 Explanations Referencing Exclusion by Age",
    x = "Age (Months)",
    y = "Explanations Referencing Exclusion"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )

EX_count_age_scatter
#Also the actual possible range of responses is 0-12, so this graph would look even worse zoomed out
```

```{r SG-count-age-scatter}
SG_count_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = SG_total)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 2 Explanations Referencing the Game Specifically by Age",
    x = "Age (Months)",
    y = "Explanations Referencing the Game Specifically"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )

SG_count_age_scatter
```

# Did a Ppt Use Type of Explanation in Any Response?

## Initial Graphs

```{r explain-present-scatter}
seas2_pivoted <- seas2_pivoted |>
  mutate(
    present = if_else(total == 0, 0, 1), 
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")
  )

seas2_pivoted|>
  ggplot(aes(x = age_months, y = present, color = explanation_type, fill = explanation_type)) +
  geom_point(position = position_jitter(height = .15)) +
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Types of Explanations Present in Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses Present Across Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(breaks = c(0, 1), labels = (c("Absent", "Present")))
```

```{r explain-present-scatter-faceted}
seas2_pivoted |>
  ggplot(aes(x = age_months, y = present, color = explanation_type, fill = explanation_type)) +
  geom_point(position = position_jitter(height = .15)) +
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  facet_wrap(~explanation_type) +
  labs(
    title = "Study 2 Types of Explanations Present in Participants' Responses", #better title/explain better
    x = "Age (Months)",
    y = "Responses Present Across Explanation Questions",
    color = "Explanations",
    fill = "Explanations"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(breaks = c(0, 1), labels = (c("Absent", "Present")))
```

## Analyses

### Overall

```{r explain-present-lmer}
summary(lmer(
  present ~ age_months * explanation_type + (1 | subject),
  data = seas2_pivoted
)) #Again, I thought this would be a binomial glmer but errors; however lmer output doesn't seem to match graphs
```

In this model, the presence of a type of explanation across a participant's responses significantly differs based on age, IN, age x EN, and age x OR.

### Exclusion

```{r EX-present-age-glm}
#Does the presence of explanations that reference exclusion change with age?

seas2_separated <- seas2_separated |>
  mutate(
    across(
      .cols = ST_total:OR_total,
      .fns = ~if_else(.x > 0, 1, 0),
      .names = "{sub('total', 'present', col)}"
    )
  ) #Adding present columns to non-pivoted dataset


summary(glm(
  EX_present ~ age_months,
  data = seas2_separated
))
```

Whether participants reference exclusion at least once in the study significantly differs with age.

### Inclusion

```{r IN-present-age-glm}
#Does the presence of explanations that reference inclusion change with age?
summary(glm(
  IN_present ~ age_months,
  data = seas2_separated
))
```

Whether participants reference inclusion at least once in the study significantly differs with age.

### Negative Evaluations

```{r EN-present-age-glm}
#Does the presence of explanations that reference negative evaluations change with age?
summary(glm(
  EN_present ~ age_months,
  data = seas2_separated
))
```

Whether participants reference negative evaluations at least once in the study does not significantly differ with age.

### Other

```{r OR-present-age-glm}
#Does the presence of explanations that reference something not categorized in our codes change with age?
summary(glm(
  OR_present ~ age_months,
  data = seas2_separated
))
```

Whether participants answer with something not contained in our explanation codes at least once in the study does not significantly differ with age.

### Superficial Traits

```{r ST-present-age-glm}
#Does the presence of explanations that reference superficial traits change with age?
summary(glm(
  ST_present ~ age_months,
  data = seas2_separated
))
```

Whether participants reference superficial traits at least once in the study significantly differs with age.

### Specific Game

```{r SG-present-age-glm}
#Does the presence of explanations that reference the game specifically change with age?
summary(glm(
  SG_present ~ age_months,
  data = seas2_separated
))
```

Whether participants reference the game specifically at least once in the study significantly differs with age.

### Friends

```{r FR-present-age-glm}
#Does the presence of explanations that reference preferences change with age?
summary(glm(
  FR_present ~ age_months,
  data = seas2_separated
))
```

Whether participants reference friends at least once in the study does not significantly differ with age.

### Possessions

```{r PS-present-age-glm}
#Does the presence of explanations that reference preferences change with age?
summary(glm(
  PS_present ~ age_months,
  data = seas2_separated
))
```

Whether participants reference possessions at least once in the study does not significantly differ with age.

## Follow-Up Graphs

```{r EX-presence-age-scatter}
EX_presence_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = EX_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 2 Explanations Referencing Exclusion by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Exclusion Referenced")
    )

EX_presence_age_scatter
```

```{r IN-presence-age-scatter}
IN_presence_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = IN_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 2 Explanations Referencing Inclusion by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Inclusion Referenced")
    )

IN_presence_age_scatter
```

```{r SG-presence-age-scatter}
SG_presence_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = SG_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 2 Explanations Referencing the Game Specifically by Age",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Specific Game Referenced")
    )

SG_presence_age_scatter
```

# Word Count

## Graphs

```{r word-scatter}
#Scatterplot of total word count by age

seas2 |>
  rowwise() |>
  mutate(
    word_total = sum(c_across(contains("word"))) #could remove NAs from this step, but it's actually probably better to drop NAs from the scatter bc don't know how many words MS people would have
  ) |>
  ungroup() |>
  ggplot(aes(x = age_months, y = word_total)) +
  geom_point() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 2 Explanation Total Word Count by Age",
    x = "Age (Months)",
    y = "Word Count"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )
```

## Analyses

```{r word-lm}
seas2_wordtot <- seas2 |>
  rowwise() |>
  mutate(
    word_total = sum(c_across(contains("word")))) |>
  filter(!is.na(word_total))

summary(glm(
  word_total ~ age_months,
  data = seas2_wordtot
))
```

The number of words used by participants significantly differs based on age.
