---
title: "04 SEAS Study 2 Explanatory Analyses"
format: html
author: Siobhan Crowley
date: 04/11/2026
editor: source
editor_options: 
  chunk_output_type: console
---

# Packages
```{r packages, message = FALSE, warning = FALSE}
library(readxl)
library(tidyverse)
library(lme4)
library(lmerTest)
library(showtext)
library(viridis)
library(chisq.posthoc.test)
library(Hmisc)
library(gt)
library(webshot2)

showtext_auto()
```

# Data Preparation
```{r data-colors}
magma_colors <- c("#000004FF", "#180F3EFF", "#451077FF", "#721F81FF", "#9F2F7FFF", "#CD4071FF", "#F1605DFF", "#FD9567FF", "#FEC98DFF", "#FCFDBFFF") #from magma(10)

wo_black <- viridis::magma(20)[5:20]
```

```{r data-load}
seas2_full <- read_excel("../Data/FINAL SEAS V2 Dataset.xlsx")

seas2 <- subset(seas2_full, final_data == "Y") # dropping excluded participants
```

```{r data-init-prep}
seas2 <- seas2 |>
  mutate(
    DOB = make_date(birth_year, birth_month, birth_day), #creating date of birth and date of test columns
    DOT = as_date(DOT),
    .before = DOT
  ) |>
  mutate(
    age_months = interval(DOB, DOT) %/% months(1), .after = DOT #calculating age in months
  )
```

```{r data-main-prep}
#Combining any explanation code for a particular response
seas2_united <- seas2 |>
  unite("status_explain_1", status_storyref_1:status_relation_1, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_1", resource_storyref_1:resource_relation_1, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_2", status_storyref_2:status_relation_2, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_2", resource_storyref_2:resource_relation_2, sep  = " ", na.rm = TRUE) |>
   unite("status_explain_comp1", comp_status_storyref_1:comp_status_relation_1, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_comp1", comp_resource_storyref_1:comp_resource_relation_1, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_3", status_storyref_3:status_relation_3, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_3", resource_storyref_3:resource_relation_3, sep  = " ", na.rm = TRUE) |>
  unite("status_explain_4", status_storyref_4:status_relation_4, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_4", resource_storyref_4:resource_relation_4, sep  = " ", na.rm = TRUE) |>
unite("status_explain_comp2", comp_status_storyref_2:comp_status_relation_2, sep = " ", na.rm = TRUE) |>
  unite("resource_explain_comp2", comp_resource_storyref_2:comp_resource_relation_2, sep  = " ", na.rm = TRUE)
```

```{r explain-map-func}
#Creating a general explanation mapping function
individual_explain_func <- function(status_or_resource, trial_num) {
  
  possible_explain <- c("ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")
  
  column_of_interest <- paste0(status_or_resource, "_explain_", trial_num)
  
  list_of_dfs <- purrr::map(possible_explain, function(explain) {
    seas2_united |>
      mutate(!!paste0(status_or_resource, "_", explain, "_", trial_num) := if_else(str_detect(.data[[column_of_interest]], explain), 1, 0))
  })
    
    selected_cols <- map(list_of_dfs, ~select(., subject, last_col()))
    
    reduce(selected_cols, left_join, by = "subject")
  }
```

```{r explain-columns}
#Gathering individual explanation columns for each response
seas2_status_1 <- individual_explain_func("status", 1)
seas2_resource_1 <- individual_explain_func("resource", 1)
seas2_status_2 <- individual_explain_func("status", 2)
seas2_resource_2 <- individual_explain_func("resource", 2)
seas2_status_comp1 <- individual_explain_func("status", "comp1")
seas2_resource_comp1 <- individual_explain_func("resource", "comp1")
seas2_status_3 <- individual_explain_func("status", 3)
seas2_resource_3 <- individual_explain_func("resource", 3)
seas2_status_4 <- individual_explain_func("status", 4)
seas2_resource_4 <- individual_explain_func("resource", 4)
seas2_status_comp2 <- individual_explain_func("status", "comp2")
seas2_resource_comp2 <- individual_explain_func("resource", "comp2")

#Combining back into one dataframe
seas2_separated <- seas2_united |>
  left_join(seas2_status_1, by = "subject") |>
  left_join(seas2_resource_1, by = "subject") |>
  left_join(seas2_status_2, by = "subject") |>
  left_join(seas2_resource_2, by = "subject") |>
  left_join(seas2_status_comp1, by = "subject") |>
  left_join(seas2_resource_comp1, by = "subject") |>
  left_join(seas2_status_3, by = "subject") |>
  left_join(seas2_resource_3, by = "subject") |>
  left_join(seas2_status_4, by = "subject") |>
  left_join(seas2_resource_4, by = "subject") |>
  left_join(seas2_status_comp2, by = "subject") |>
  left_join(seas2_resource_comp2, by = "subject")
```

```{r sum-scores}
#Creating sum scores for each type of explanation
seas2_separated <- seas2_separated |>
  rowwise() |>
  mutate(
    ST_total = sum(c_across(matches(".*_ST_."))),
    VG_total = sum(c_across(matches(".*_VG_."))),
    SG_total = sum(c_across(matches(".*_SG_."))),
    EX_total = sum(c_across(matches(".*_EX_."))),
    IN_total = sum(c_across(matches(".*_IN_."))),
    NR_total = sum(c_across(matches(".*_NR_."))),
    MR_total = sum(c_across(matches(".*_MR_."))),
    AR_total = sum(c_across(matches(".*_AR_."))),
    EP_total = sum(c_across(matches(".*_EP_."))),
    EN_total = sum(c_across(matches(".*_EN_."))),
    PR_total = sum(c_across(matches(".*_PR_."))),
    EM_total = sum(c_across(matches(".*_EM_."))),
    MT_total = sum(c_across(matches(".*_MT_."))),
    FR_total = sum(c_across(matches(".*_FR_."))),
    PS_total = sum(c_across(matches(".*_PS_."))),
    OR_total = sum(c_across(matches(".*_OR_."))),
    ) |>
  ungroup() 
```

```{r pivot-explain}
#Pivoting explanation type
seas2_pivoted <- seas2_separated |>
  pivot_longer(ST_total:OR_total, names_to = "explanation_type", names_pattern = "(..)_total", values_to = "total")
```

```{r frequency-table}
#Some exploration of frequency of each type of explanation
seas2_pivoted |>
  group_by(explanation_type) |>
  dplyr::summarize(
    max = max(total),
    min = min(total),
    mean = mean(total)
  )
```

# Basic Answer Categorization
## Graphs
```{r answer-col}
seas2_answer_col <- seas2 |>
  pivot_longer(
    cols = contains("response"),
    names_to = "trial",
    values_to = "response"
  ) |>
  ggplot(aes(x = as.factor(age), fill = fct_rev(response))) +
    geom_bar(position = "fill") +
    scale_fill_manual(
      values = c(magma_colors[7], magma_colors[5], magma_colors[3]),
      labels = c("Relevant Answer", "No or Irrelevant Answer", "Missing")
      ) +
    labs(
      title = "Study 2 Explanations Given by Age",
      x = "Age (Years)",
      y = "Proportion",
      fill = NULL
    ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    legend.position = "top",
    text = element_text(family = "serif", size = 25)
        )

seas2_answer_col
```

## Analyses
```{r answer-chi}
seas2_response <- seas2 |>
  pivot_longer(
    cols = contains("response"),
    names_to = "trial",
    values_to = "response"
  )

seas2_response_table <- xtabs(~response + age, data = seas2_response)

seas2_response_chi <- chisq.test(seas2_response_table)

seas2_response_chi

seas2_response_posthoc <- chisq.posthoc.test(seas2_response_table, method = "bonferroni")

seas2_response_posthoc

seas2_response_posthoc <- seas2_response_posthoc |>
  rename(
    three = `3`,
    four = `4`,
    five = `5`,
    six = `6`
  )
```

A chi-square square test of independence found that there was a difference across age groups for the overall type of response participants gave to explanation questions (no or irrelevant answer, relevant answer, or missing data). Chi-squared = `r round(unname(seas2_response_chi$statistic), 2)`, df = `r unname(seas2_response_chi$parameter)`, p = `r signif(seas2_response_chi$p.value, 2)`.

A post-hoc test with Bonferroni correction found one significant difference in whether the response data was missing across age (p~3~ = `r seas2_response_posthoc$three[2]`, p~4~ = `r seas2_response_posthoc$four[2]`, p~5~ = `r signif(seas2_response_posthoc$five[2], 2)`, p~6~ = `r seas2_response_posthoc$six[2]`), with 5-year-olds having fewer missing responses than would be expected (adjusted residual = `r round(seas2_response_posthoc$five[1])`), likely due to the fact that there are no missing responses among this age group. 

Additionally, there were significant differences in no/irrelevant responses and relevant responses. For no/irrelevant responses, ages 3 and 6 were significant while 4 and 5 were not (p~3~ = `r seas2_response_posthoc$three[4]`, p~4~ = `r seas2_response_posthoc$four[4]`, p~5~ = `r signif(seas2_response_posthoc$five[4], 2)`, p~6~ = `r seas2_response_posthoc$six[4]`). The standardized residuals demonstrate that this difference stems from 3-year olds having a greater number of no/irrelevant responses and 6-year olds having fewer than would be expected. (residual~3~ = `r round(seas2_response_posthoc$three[3], 2)`, residual~6~ = `r round(seas2_response_posthoc$six[3], 2)`). A slightly different pattern is found for relevant answers, with 3- and 5-year-old being the only significant groups, such that 5-year-olds have a greater number and 3-year-olds fewer  (p~3~ = `r seas2_response_posthoc$three[6]`, residual~3~ = `r round(seas2_response_posthoc$three[5], 2)`; p~5~ = `r seas2_response_posthoc$five[6]`, residual~5~ = `r round(seas2_response_posthoc$five[5], 2)`).

# Number of Times a Ppt Used Explanation Across Each Response (0-12)
## Initial Graphs
```{r explain-count-basiccol}
#Column chart to see the total number of each type of explanation category participants used across their 12 explanation questions (explain better; can use multiple types of explanation in one response, but using that explanation in response will only be counted once for each question--i.e. maximum for each category is 12)

seas2_pivoted |>
  ggplot(aes(x = as.factor(age), y = total, fill = explanation_type)) +
  geom_col()
```

```{r explain-count-scatter-faceted}
seas2_pivoted |>
  mutate(
    explanation_type = fct_relevel(explanation_type, "ST", "VG", "SG", "EX", "IN", "NR", "MR", "AR", "EP", "EN", "PR", "EM", "MT", "FR", "PS", "OR")) |>
  ggplot(aes(x = age_months, y = total, color = explanation_type, fill = explanation_type)) +
  geom_jitter() +
  geom_smooth(method = "lm", alpha = 0.2) +
  facet_wrap(~explanation_type) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  labs(
    title = "Study 2 Frequency of Explanation Types",
    x = "Age (Months)",
    y = "Number of Responses",
    color = "Explanation Types",
    fill = "Explanation Types"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        )
```

## GLMMs
### Overall
```{r explain-count-lmer}
# CHECK
#Does the frequency of each answer type change with age?
seas2_count_lmer <- summary(lmer(
  total ~ age_months * explanation_type + (1 | subject),
  data = seas2_pivoted
)) #lmer correct? I thought it would be glmer with a poisson family but that produced errors

seas2_count_lmer
```

In this model, SG x age (p = `r signif(seas2_count_lmer$coefficients[30,5], 2)`) and ST x age (p = `r signif(seas2_count_lmer$coefficients[31,5], 2)`) are significant, demonstrating that the frequencies of explanation responses (0-12 across trial) change with these conditions.

### Exclusion
```{r EX-count-age-glm}
#Does the frequency of explanations that reference exclusion change with age?
seas2_EX_count_age <- summary(glm(
  EX_total ~ age_months,
  data = seas2_separated
))

seas2_EX_count_age
```

The number of explanations that reference exclusion given by participants does significantly differ by age, t = `r round(seas2_EX_count_age$coefficients[2,3], 2)`, p = `r signif(seas2_EX_count_age$coefficients[2,4], 2)`, such that as age increases, so does the frequency of responses referencing exclusion.

```{r EX-count-QType-glm}
#Does whether a response references exclusion depend on the question type (status or resources), age, or the interaction thereof?
seas2_EX_qtype <- seas2_separated |>
  select(subject, age_months, matches(".*_EX_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_EX_.",
    values_to = "EX"
  )

summary(glm(
  EX ~ question_type * age_months,
  data = seas2_EX_qtype
))
```

According to this model, the number of explanations that reference exclusion differs based on age, but not based on the type of question (status vs resources) or an interaction between the two.

```{r EX-count-age-scatter}
EX_count_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = EX_total)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 2 Frequency of Exclusion Explanations",
    x = "Age (Months)",
    y = "Explanations Referencing Exclusion"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  coord_cartesian(ylim = c(0, 12)) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12))

EX_count_age_scatter
```

### Inclusion
```{r IN-count-age-glm}
#Does the frequency of explanations that reference inclusion change with age?
seas2_IN_count_age <- summary(glm(
  IN_total ~ age_months,
  data = seas2_separated
))

seas2_IN_count_age
```

The number of explanations that reference inclusion given by participants does significantly differ by age, t = `r round(seas2_IN_count_age$coefficients[2,3], 2)`, p = `r signif(seas2_IN_count_age$coefficients[2,4], 2)`.

```{r IN-count-QType-glm}
#Does whether a response references inclusion depend on the question type (status or resources), age, or the interaction thereof?
seas2_IN_qtype <- seas2_separated |>
  select(subject, age_months, matches(".*_IN_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_IN_.",
    values_to = "IN"
  )

summary(glm(
  IN ~ question_type * age_months,
  data = seas2_IN_qtype
))
```

According to this model, the number of explanations that reference inclusion differs based on age, but not based on the type of question (status vs resources) or an interaction between the two.

```{r IN-count-age-scatter}
IN_count_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = IN_total)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 2 Frequency of Inclusion Explanations",
    x = "Age (Months)",
    y = "Explanations Referencing Inclusion"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  coord_cartesian(ylim = c(0, 12)) +
  scale_y_continuous(breaks = c(0, 2, 4, 6, 8, 10, 12))

IN_count_age_scatter
```

### Specific Game
```{r SG-count-age-glm}
#Does the frequency of explanations that reference the game specifically change with age?
seas2_SG_count_age <- summary(glm(
  SG_total ~ age_months,
  data = seas2_separated
))

seas2_SG_count_age
```

The number of explanations that reference the game with specific details given by participants does significantly differ by age, t = `r round(seas2_SG_count_age$coefficients[2,3], 2)`, p = `r signif(seas2_SG_count_age$coefficients[2,4], 2)`.

```{r SG-count-QType-glm}
#does whether a response references the game specifically depend on the question type (status or resources), age, or the interaction thereof?
seas2_SG_qtype <- seas2_separated |>
  select(subject, age_months, matches(".*_SG_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_SG_.",
    values_to = "SG"
  )

summary(glm(
  SG ~ question_type * age_months,
  data = seas2_SG_qtype
))
```

Whether an answer references the game specifically is significantly associated with age but not question type nor an interaction between age and question type.

```{r SG-count-age-scatter}
SG_count_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = SG_total)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 2 Frequency of Specific Game Explanations",
    x = "Age (Months)",
    y = "Explanations Referencing the Game Specifically"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )

SG_count_age_scatter
```

### Superficial Traits
```{r ST-count-age-glm}
#Does the frequency of explanations that reference the game specifically change with age?
seas2_ST_count_age <- summary(glm(
  ST_total ~ age_months,
  data = seas2_separated
))

seas2_ST_count_age
```

The number of explanations that reference superficial traits about a character given by participants does not significantly differ by age, p = `r signif(seas2_ST_count_age$coefficients[2,4], 2)`.

```{r ST-count-QType-glm}
#Does whether a response references the game specifically depend on the question type (status or resources), age, or the interaction thereof?
seas2_ST_qtype <- seas2_separated |>
  select(subject, age_months, matches(".*_ST_.")) |>
  pivot_longer(
    cols = -(subject:age_months),
    names_to = "question_type",
    names_pattern = "(.*)_ST_.",
    values_to = "ST"
  )

summary(glm(
  ST ~ question_type * age_months,
  data = seas2_ST_qtype
))
```

Whether an answer references a character's superficial traits is not significantly associated with age, question type, or an interaction between the two.

## Correlations
### Exclusion Status
```{r explain-count-exstatus-cor}
seas2_separated <- seas2_separated |> #adding exclusion status total score to this dataset
  mutate(
    exclusion_video_selection = case_when(
      interaction_1 == "exclusion" ~ status_1, 
      interaction_2 == "exclusion" ~ status_2
    ),
    exclusion_story_selection = case_when(
      interaction_3 == "exclusion" ~ status_3, 
      interaction_4 == "exclusion" ~ status_4
    )
  ) |> #select exclusion from videos and stories
  mutate(across(
    .cols = c(exclusion_video_selection, exclusion_story_selection),
    .fns = ~if_else(.x == "excluder", 1, 0)
  )) |> #convert numeric
  rowwise() |>
  mutate(
    exclusion_status_total = sum(c_across(c(exclusion_video_selection, exclusion_story_selection)))
  ) |> #sum
  ungroup()

seas2_count_exstatus_cor_data <- seas2_separated |>
  select(exclusion_status_total, ST_total:OR_total)

seas2_count_exstatus_cor_matrix <- rcorr(as.matrix(seas2_count_exstatus_cor_data), type = "spearman")

seas2_count_exstatus_correlation <- seas2_count_exstatus_cor_matrix$r[1, -1]
seas2_count_exstatus_p <- seas2_count_exstatus_cor_matrix$P[1, -1]

seas2_count_exstatus_df <- data.frame(rho = seas2_count_exstatus_correlation, p = seas2_count_exstatus_p)

seas2_count_exstatus_df <- seas2_count_exstatus_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas2_count_exstatus_table <- seas2_count_exstatus_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "blue") |>
    tab_header(title = "Exclusion Status Total & Explanation Type Frequency Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas2_count_exstatus_table

gtsave(seas2_count_exstatus_table, "04-SEAS-Study-2-Explanatory-Analyses_files/figure-html/seas2_count_exstatus_table.png")
```

Specific Game and Exclusion were the only explanation types whose frequencies displayed a significant correlation with the number of times a participant selected the excluder as being in charge in the exclusion trials. SG: rho = `r signif(unname(seas2_count_exstatus_correlation[3]), 2)` (weak positive), p = `r signif(unname(seas2_count_exstatus_p[3]), 2)`, p with Bonferroni correction = `r signif(seas2_count_exstatus_p[3] * 16, 2)`. EX: rho = `r signif(unname(seas2_count_exstatus_correlation[4]), 2)` (weak positive), p = `r signif(unname(seas2_count_exstatus_p[4]), 2)`, p with Bonferroni correction = `r signif(seas2_count_exstatus_p[4] * 16, 2)`.

### Comparison Status
```{r explain-count-compstatus-cor}
seas2_separated <- seas2_separated |> #adding comp status total
   mutate(
    comp_status_1_num = if_else(comp_status_1 == "excluder", 1, 0),
    comp_status_2_num = if_else(comp_status_2 == "excluder", 1, 0),
    comp_status_total = comp_status_1_num + comp_status_2_num
  )

seas2_count_compstatus_cor_data <- seas2_separated |>
  select(comp_status_total, ST_total:OR_total)

seas2_count_compstatus_cor_matrix <- rcorr(as.matrix(seas2_count_compstatus_cor_data), type = "spearman")

seas2_count_compstatus_correlation <- seas2_count_compstatus_cor_matrix$r[1, -1]
seas2_count_compstatus_p <- seas2_count_compstatus_cor_matrix$P[1, -1]

seas2_count_compstatus_df <- data.frame(rho = seas2_count_compstatus_correlation, p = seas2_count_compstatus_p)

seas2_count_compstatus_df <- seas2_count_compstatus_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas2_count_compstatus_table <- seas2_count_compstatus_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "cyan") |>
    tab_header(title = "Comparison Status Total & Explanation Type Frequency Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas2_count_compstatus_table

gtsave(seas2_count_compstatus_table, "04-SEAS-Study-2-Explanatory-Analyses_files/figure-html/seas2_count_compstatus_table.png")
```

The number of explanations including preferences significantly correlated with the number of times a participant selected the excluder over the includer as being in charge, rho = `r signif(unname(seas2_count_compstatus_correlation[11]), 2)` (weak negative), p = `r signif(unname(seas2_count_compstatus_p[11]), 2)`, p with Bonferroni correction = `r signif(seas2_count_compstatus_p[11] * 16, 2)`.

### Exclusion Resources
```{r explain-count-exresources-cor}
seas2_separated <- seas2_separated |> #adding exclusion resources total
  mutate(
    exclusion_physical_selection = case_when(
      interaction_1 == "exclusion" & resource_type_1 == "physical" ~ resource_1, 
      interaction_2 == "exclusion" & resource_type_2 == "physical" ~ resource_2,
      interaction_3 == "exclusion" & resource_type_3 == "physical" ~ resource_3,
      interaction_4 == "exclusion" & resource_type_4 == "physical" ~ resource_4
    ),
    exclusion_social_selection = case_when(
      interaction_1 == "exclusion" & resource_type_1 == "social" ~ resource_1, 
      interaction_2 == "exclusion" & resource_type_2 == "social" ~ resource_2,
      interaction_3 == "exclusion" & resource_type_3 == "social" ~ resource_3,
      interaction_4 == "exclusion" & resource_type_4 == "social" ~ resource_4
    )
  ) |> #pull out physical and social excluder selection responses
  mutate(across(
    .cols = c(exclusion_physical_selection, exclusion_social_selection),
    .fns = ~if_else(.x == "excluder", 1, 0)
  )) |> #convert to numeric
  rowwise() |>
  mutate(
    exclusion_resource_total = exclusion_physical_selection + exclusion_social_selection
  ) |>
  ungroup() #create total resources score 

seas2_count_exresource_cor_data <- seas2_separated |>
  select(exclusion_resource_total, ST_total:OR_total)

seas2_count_exresource_cor_matrix <- rcorr(as.matrix(seas2_count_exresource_cor_data), type = "spearman")

seas2_count_exresource_correlation <- seas2_count_exresource_cor_matrix$r[1, -1]
seas2_count_exresource_p <- seas2_count_exresource_cor_matrix$P[1, -1]

seas2_count_exresource_df <- data.frame(rho = seas2_count_exresource_correlation, p = seas2_count_exresource_p)

seas2_count_exresource_df <- seas2_count_exresource_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas2_count_exresource_table <- seas2_count_exresource_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "pink") |>
    tab_header(title = "Exclusion Resource Total & Explanation Type Frequency Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas2_count_exresource_table

gtsave(seas2_count_exresource_table, "04-SEAS-Study-2-Explanatory-Analyses_files/figure-html/seas2_count_exresource_table.png")
```

Emotion was the only explanation type whose frequencies displayed a significant correlation with the number of times a participant selected the excluder as having more resources in the exclusion trials, rho = `r signif(unname(seas2_count_exresource_correlation[12]), 2)` (weak negative), p = `r signif(unname(seas2_count_exresource_p[12]), 2)`, p with Bonferroni correction = `r signif(seas2_count_exresource_p[12] * 16, 2)`.

### Comparison Resources
```{r explain-count-compresources-cor}
seas2_separated <- seas2_separated |> #adding comp resources total
  mutate(
    comp_physical_selection = if_else(comp_resource_type_1 == "physical", comp_resource_1, comp_resource_2),
    comp_social_selection = if_else(comp_resource_type_1 == "social", comp_resource_1, comp_resource_2)
  ) |>
  mutate(
    across(
      .cols = c(comp_physical_selection, comp_social_selection), 
      .fns = ~if_else(.x == "excluder", 1, 0)
    ),
    comp_resource_total = comp_physical_selection + comp_social_selection
  )


seas2_count_compresource_cor_data <- seas2_separated |>
  select(comp_resource_total, ST_total:OR_total)

seas2_count_compresource_cor_matrix <- rcorr(as.matrix(seas2_count_compresource_cor_data), type = "spearman")

seas2_count_compresource_correlation <- seas2_count_compresource_cor_matrix$r[1, -1]
seas2_count_compresource_p <- seas2_count_compresource_cor_matrix$P[1, -1]

seas2_count_compresource_df <- data.frame(rho = seas2_count_compresource_correlation, p = seas2_count_compresource_p)

seas2_count_compresource_df <- seas2_count_compresource_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas2_count_compresource_table <- seas2_count_compresource_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "red") |>
    tab_header(title = "Comparison Resource Total & Explanation Type Frequency Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas2_count_compresource_table

gtsave(seas2_count_compresource_table, "04-SEAS-Study-2-Explanatory-Analyses_files/figure-html/seas2_count_compresource_table.png")
```

There were no significant correlations between frequencies of explanation type and number of times selecting the excluder over the includer as having more resources.

# Did a Ppt Use Type of Explanation in Any Response?
## Initial Graphs
```{r explain-present-scatter-faceted}
seas2_pivoted <- seas2_pivoted |>
  mutate(
    present = if_else(total == 0, 0, 1)
  )

seas2_pivoted |>
  ggplot(aes(x = age_months, y = present, color = explanation_type, fill = explanation_type)) +
  geom_point(position = position_jitter(height = .15)) +
  geom_smooth(method = "lm", alpha = 0.2) +
  scale_fill_manual(values = wo_black) +
  scale_color_manual(values = wo_black) +
  facet_wrap(~explanation_type) +
  labs(
    title = "Study 2 Presence of Explanation Types",
    x = "Age (Months)",
    y = "Response Presence",
    color = "Explanation Types",
    fill = "Explanation Types"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(breaks = c(0, 1), labels = (c("Absent", "Present")))
```

## GLMMs
### Overall
```{r explain-present-lmer}
#CHECK
seas2_present_lmer <- summary(lmer(
  present ~ age_months * explanation_type + (1 | subject),
  data = seas2_pivoted
)) #Again, I thought this would be a binomial glmer but errors; however lmer output doesn't seem to match graphs

seas2_present_lmer
```

In this model, the presence of a type of explanation across a participant's responses significantly differs based on EX (p = `r signif(seas2_present_lmer$coefficients[6,5], 2)`), IN (p = `r signif(seas2_present_lmer$coefficients[8,5], 2)`), age x EX (p = `r signif(seas2_present_lmer$coefficients[21,5], 2)`), age x IN (p = `r signif(seas2_present_lmer$coefficients[23,5], 2)`), and age x SG (p = `r signif(seas2_present_lmer$coefficients[30,5], 2)`).

### Exclusion
```{r EX-present-age-glm}
#Does the presence of explanations that reference exclusion change with age?

seas2_separated <- seas2_separated |> #Adding present columns to non-pivoted dataset
  mutate(
    across(
      .cols = ST_total:OR_total,
      .fns = ~if_else(.x > 0, 1, 0),
      .names = "{sub('total', 'present', col)}"
    )
  )

seas2_EX_present_age <- summary(glm(
  EX_present ~ age_months,
  data = seas2_separated
))

seas2_EX_present_age
```

Whether participants reference exclusion at least once in the study significantly differs with age, t = `r round(seas2_EX_present_age$coefficients[2,3], 2)`, p = `r signif(seas2_EX_present_age$coefficients[2,4], 2)`.

```{r EX-present-age-scatter}
EX_present_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = EX_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 2 Presence of Exclusion Explanations",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Exclusion Referenced")
    )

EX_present_age_scatter
```

### Inclusion
```{r IN-present-age-glm}
#Does the presence of explanations that reference inclusion change with age?
seas2_IN_present_age <- summary(glm(
  IN_present ~ age_months,
  data = seas2_separated
))

seas2_IN_present_age
```

Whether participants reference inclusion at least once in the study significantly differs with age, t = `r round(seas2_IN_present_age$coefficients[2,3], 2)`, p = `r signif(seas2_IN_present_age$coefficients[2,4], 2)`.

```{r IN-present-age-scatter}
IN_present_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = IN_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 2 Presence of Inclusion Explanations",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Inclusion Referenced")
    )

IN_present_age_scatter
```

### Specific Game
```{r SG-present-age-glm}
#Does the presence of explanations that reference the game specifically change with age?
seas2_SG_present_age <- summary(glm(
  SG_present ~ age_months,
  data = seas2_separated
))

seas2_SG_present_age
```

Whether participants reference the game specifically at least once in the study significantly differs with age, t = `r round(seas2_SG_present_age$coefficients[2,3], 2)`, p = `r signif(seas2_SG_present_age$coefficients[2,4], 2)`.

```{r SG-present-age-scatter}
SG_present_age_scatter <- seas2_separated |>
  ggplot(aes(x = age_months, y = SG_present)) +
  geom_jitter() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  geom_hline(yintercept = 0.5, linetype = "dashed", linewidth = 1, alpha = 0.5) +
  labs(
    title = "Study 2 Presence of Specific Game Explanations",
    x = "Age (Months)",
    y = NULL
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        ) +
  scale_y_continuous(
    breaks = c(0,1),
    labels = c("Not Referenced", "Specific Game Referenced")
    )

SG_present_age_scatter
```

## Correlations
### Exclusion Status
```{r explain-present-exstatus-cor}
seas2_present_exstatus_cor_data <- seas2_separated |>
  select(exclusion_status_total, ST_present:OR_present)

seas2_present_exstatus_cor_matrix <- rcorr(as.matrix(seas2_present_exstatus_cor_data), type = "spearman")

seas2_present_exstatus_correlation <- seas2_present_exstatus_cor_matrix$r[1, -1]
seas2_present_exstatus_p <- seas2_present_exstatus_cor_matrix$P[1, -1]

seas2_present_exstatus_df <- data.frame(rho = seas2_present_exstatus_correlation, p = seas2_present_exstatus_p)

seas2_present_exstatus_df <- seas2_present_exstatus_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas2_present_exstatus_table <- seas2_present_exstatus_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "blue") |>
    tab_header(title = "Exclusion Status Total & Explanation Type Presence Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas2_present_exstatus_table

gtsave(seas2_present_exstatus_table, "04-SEAS-Study-2-Explanatory-Analyses_files/figure-html/seas2_present_exstatus_table.png")
```

Superficial Traits and Exclusion were the only explanation types whose presence/absence displayed a significant correlation with the number of times a participant selected the excluder as being in charge in the exclusion trials. ST: rho = `r signif(unname(seas2_present_exstatus_correlation[1]), 2)` (weak positive), p = `r signif(unname(seas2_present_exstatus_p[1]), 2)`, p with Bonferroni correction = `r signif(seas2_present_exstatus_p[1] * 16, 2)`. EX: rho = `r signif(unname(seas2_present_exstatus_correlation[4]), 2)` (weak positive), p = `r signif(unname(seas2_present_exstatus_p[4]), 2)`, p with Bonferroni correction = `r signif(seas2_present_exstatus_p[4] * 16, 2)`.

### Comparison Status
```{r explain-present-compstatus-cor}
seas2_present_compstatus_cor_data <- seas2_separated |>
  select(comp_status_total, ST_present:OR_present)

seas2_present_compstatus_cor_matrix <- rcorr(as.matrix(seas2_present_compstatus_cor_data), type = "spearman")

seas2_present_compstatus_correlation <- seas2_present_compstatus_cor_matrix$r[1, -1]
seas2_present_compstatus_p <- seas2_present_compstatus_cor_matrix$P[1, -1]

seas2_present_compstatus_df <- data.frame(rho = seas2_present_compstatus_correlation, p = seas2_present_compstatus_p)

seas2_present_compstatus_df <- seas2_present_compstatus_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas2_present_compstatus_table <- seas2_present_compstatus_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "cyan") |>
    tab_header(title = "Comparison Status Total & Explanation Type Presence Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas2_present_compstatus_table

gtsave(seas2_present_compstatus_table, "04-SEAS-Study-2-Explanatory-Analyses_files/figure-html/seas2_present_compstatus_table.png")
```

Whether a participant had an explanation referencing preferences at some point in the study significantly correlated with the number of times a participant selected the excluder over the includer as being in charge, rho = `r signif(unname(seas2_present_compstatus_correlation[11]), 2)` (weak positive), p = `r signif(unname(seas2_present_compstatus_p[11]), 2)`, p with Bonferroni correction = `r signif(seas2_present_compstatus_p[11] * 16, 2)`.

### Exclusion Resources
```{r explain-present-exresources-cor}
seas2_present_exresource_cor_data <- seas2_separated |>
  select(exclusion_resource_total, ST_present:OR_present)

seas2_present_exresource_cor_matrix <- rcorr(as.matrix(seas2_present_exresource_cor_data), type = "spearman")

seas2_present_exresource_correlation <- seas2_present_exresource_cor_matrix$r[1, -1]
seas2_present_exresource_p <- seas2_present_exresource_cor_matrix$P[1, -1]

seas2_present_exresource_df <- data.frame(rho = seas2_present_exresource_correlation, p = seas2_present_exresource_p)

seas2_present_exresource_df <- seas2_present_exresource_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas2_present_exresource_table <- seas2_present_exresource_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "pink") |>
    tab_header(title = "Exclusion Resource Total & Explanation Type Presence Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas2_present_exresource_table

gtsave(seas2_present_exresource_table, "04-SEAS-Study-2-Explanatory-Analyses_files/figure-html/seas2_present_exresource_table.png")
```

Emotion was the only explanation type whose presence/absence displayed a significant correlation with the number of times a participant selected the excluder as having more resources in the exclusion trials, rho = `r signif(unname(seas2_present_exresource_correlation[12]), 2)` (weak negative), p = `r signif(unname(seas2_present_exresource_p[12]), 2)`, p with Bonferroni correction = `r signif(seas2_present_exresource_p[12] * 16, 2)`.

### Comparison Resources
```{r explain-present-compresources-cor}
seas2_present_compresource_cor_data <- seas2_separated |>
  select(comp_resource_total, ST_present:OR_present)

seas2_present_compresource_cor_matrix <- rcorr(as.matrix(seas2_present_compresource_cor_data), type = "spearman")

seas2_present_compresource_correlation <- seas2_present_compresource_cor_matrix$r[1, -1]
seas2_present_compresource_p <- seas2_present_compresource_cor_matrix$P[1, -1]

seas2_present_compresource_df <- data.frame(rho = seas2_present_compresource_correlation, p = seas2_present_compresource_p)

seas2_present_compresource_df <- seas2_present_compresource_df |>
  rownames_to_column(var = "variable") |>
  mutate(
    rho = signif(rho, 2),
    p = signif(p, 2),
    "Corrected p" = if_else(p * 16 > 1, 1.0, p * 16)
  )

seas2_present_compresource_table <- seas2_present_compresource_df |>
  gt(
    rowname_col = "variable",
  )|>
    opt_stylize(style = 6, color = "red") |>
    tab_header(title = "Comparison Resource Total & Explanation Type Presence Correlations") |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      columns = c(rho, p, "Corrected p"),
      rows = p < 0.05
    )
  ) |>
  cols_align(
    align = "center",
    columns = everything()
  ) |>
  tab_footnote(
    "Significant p-values (regardless of whether corrected p was significant) have been highlighted"
  )

seas2_present_compresource_table

gtsave(seas2_present_compresource_table, "04-SEAS-Study-2-Explanatory-Analyses_files/figure-html/seas2_present_compresource_table.png")
```

The presence/absence of Vague Game and Specific Game explanations significantly correlated with the number of times the excluder was selected over the includer as having more resources. VG: rho = `r signif(unname(seas2_present_compresource_correlation[2]), 2)` (weak negative), p = `r signif(unname(seas2_present_compresource_p[2]), 2)`, p with Bonferroni correction = `r signif(seas2_present_compresource_p[2] * 16, 2)`. SG: rho = `r signif(unname(seas2_present_compresource_correlation[3]), 2)` (weak negative), p = `r signif(unname(seas2_present_compresource_p[3]), 2)`, p with Bonferroni correction = `r signif(seas2_present_compresource_p[3] * 16, 2)`.

# Word Count
## Graphs
```{r word-scatter}
#Scatterplot of total word count by age

seas2 |>
  rowwise() |>
  mutate(
    word_total = sum(c_across(contains("word"))) #could remove NAs from this step, but it's actually probably better to drop NAs from the scatter bc don't know how many words MS people would have
  ) |>
  ungroup() |>
  ggplot(aes(x = age_months, y = word_total)) +
  geom_point() +
  stat_smooth(
    method = "lm", 
    formula = y ~ x, 
    color = magma_colors[3], 
    fill = magma_colors[5], 
    alpha = 0.25) +
  labs(
    title = "Study 2 Explanation Total Word Count by Age",
    x = "Age (Months)",
    y = "Word Count"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 30),
    text = element_text(family = "serif", size = 25)
        )
```

## Analyses
```{r word-lm}
seas2_wordtot <- seas2 |>
  rowwise() |>
  mutate(
    word_total = sum(c_across(contains("word")))) |>
  filter(!is.na(word_total))

seas2_word_glm <- summary(glm(
  word_total ~ age_months,
  data = seas2_wordtot
))

seas2_word_glm
```

The number of words used by participants significantly differs based on age, t = `r round(seas2_word_glm$coefficients[2,3], 2)`, p = `r signif(seas2_word_glm$coefficients[2,4], 2)`.
