---
title: "05 SEAS Study 2 Empathy Analyses"
format: html
editor: source
editor_options: 
  chunk_output_type: console
---

# Packages
```{r packages-data, message = FALSE, warning = FALSE}
library(readxl)
library(tidyverse)
```

# Data Preparation
```{r data-load}
seas2_full <- read_excel("../Data/FINAL SEAS V2 Dataset.xlsx")

seas2 <- subset(seas2_full, final_data == "Y") # dropping excluded participants
```

```{r data-prep}
#Dates
seas2 <- seas2 |>
  mutate(
    DOB = make_date(birth_year, birth_month, birth_day), #creating date of birth and date of test columns
    DOT = as_date(DOT),
    .before = DOT
  ) |>
  mutate(
    age_months = interval(DOB, DOT) %/% months(1), .after = DOT #calculating age in months
  )

#EmQue Scores
seas2 <- seas2 |>
  mutate(across(starts_with("EQ_"), ~case_when(
    . == "Never" ~ 0,
    . == "Sometimes" ~ 1,
    . == "Often" ~ 2
  ))) |> #convert EmQue columns to numeric
  rowwise() |>
  mutate(
      EQ_total = sum(c_across(starts_with("EQ_"))),
      EQ_contagion = sum(c_across(c(EQ_1, EQ_4, EQ_7, EQ_10, EQ_13, EQ_16, EQ_19))),
      EQ_attention = sum(c_across(c(EQ_3, EQ_6, EQ_9, EQ_12, EQ_15, EQ_18, EQ_20))), 
      EQ_prosocial = sum(c_across(c(EQ_2, EQ_5, EQ_8, EQ_11, EQ_14, EQ_17))),
      .after = EQ_20
    ) |>
  ungroup()

# Memory Check
seas2 <- seas2 |>
  mutate(across(
    .cols = c(starts_with("mem_check"), starts_with("comp_mem_check")),
    .fns = ~if_else(.x == "correct", 0.5, 0)
         )) |> #convert to numeric
  mutate(
    mem_check_1 = mem_check_1A + mem_check_1B,
    mem_check_2 = mem_check_2A + mem_check_2B,
    comp_mem_check_1 = comp_mem_check_1A + comp_mem_check_1B,
    mem_check_3 = mem_check_3A + mem_check_3B,
    mem_check_4 = mem_check_4A + mem_check_4B,
    comp_mem_check_2 = comp_mem_check_2A + comp_mem_check_2B,
    mem_check_total = mem_check_1 + mem_check_2 + mem_check_3 + mem_check_4 + comp_mem_check_1 + comp_mem_check_2
  ) #sum scores

# Status
## Exclusion Trials
seas2 <- seas2 |>
  mutate(
    exclusion_video_selection = case_when(
      interaction_1 == "exclusion" ~ status_1, 
      interaction_2 == "exclusion" ~ status_2
    ),
    exclusion_story_selection = case_when(
      interaction_3 == "exclusion" ~ status_3, 
      interaction_4 == "exclusion" ~ status_4
    )
  ) |> #select exclusion from videos and stories
  mutate(across(
    .cols = c(exclusion_video_selection, exclusion_story_selection),
    .fns = ~if_else(.x == "excluder", 1, 0)
  )) |> #convert numeric
  rowwise() |>
  mutate(
    exclusion_selection_total = sum(c_across(c(exclusion_video_selection, exclusion_story_selection)))
  ) |> #sum
  ungroup()

## Comparison Trials
seas2 <- seas2 |>
  mutate(
    comp_status_1_num = if_else(comp_status_1 == "excluder", 1, 0),
    comp_status_2_num = if_else(comp_status_2 == "excluder", 1, 0),
    comp_status_total = comp_status_1_num + comp_status_2_num
  )

# Resources
## Exclusion Trials
seas2 <- seas2 |>
  mutate(
    exclusion_physical_selection = case_when(
      interaction_1 == "exclusion" & resource_type_1 == "physical" ~ resource_1, 
      interaction_2 == "exclusion" & resource_type_2 == "physical" ~ resource_2,
      interaction_3 == "exclusion" & resource_type_3 == "physical" ~ resource_3,
      interaction_4 == "exclusion" & resource_type_4 == "physical" ~ resource_4
    ),
    exclusion_social_selection = case_when(
      interaction_1 == "exclusion" & resource_type_1 == "social" ~ resource_1, 
      interaction_2 == "exclusion" & resource_type_2 == "social" ~ resource_2,
      interaction_3 == "exclusion" & resource_type_3 == "social" ~ resource_3,
      interaction_4 == "exclusion" & resource_type_4 == "social" ~ resource_4
    )
  ) |> #pull out physical and social excluder selection responses
  mutate(across(
    .cols = c(exclusion_physical_selection, exclusion_social_selection),
    .fns = ~if_else(.x == "excluder", 1, 0)
  )) |> #convert to numeric
  rowwise() |>
  mutate(
    exclusion_resource_total = exclusion_physical_selection + exclusion_social_selection
  ) |>
  ungroup() #create total resources score

## Comparison Trials
seas2 <- seas2 |>
  mutate(
    comp_physical_selection = if_else(comp_resource_type_1 == "physical", comp_resource_1, comp_resource_2),
    comp_social_selection = if_else(comp_resource_type_1 == "social", comp_resource_1, comp_resource_2)
  ) |>
  mutate(
    across(
      .cols = c(comp_physical_selection, comp_social_selection), 
      .fns = ~if_else(.x == "excluder", 1, 0)
    ),
    comp_resource_total = comp_physical_selection + comp_social_selection
  )
```

# Empathy Correlations
```{r empathy}
empathy_cols <- seas2 |>
  select(EQ_total:EQ_prosocial)

outcome_cols <- seas2 |>
  select(mem_check_total, exclusion_selection_total, comp_status_total, exclusion_resource_total, exclusion_physical_selection, exclusion_social_selection, comp_resource_total, comp_physical_selection, comp_social_selection)

empathy_cor <- cor(empathy_cols, outcome_cols, use = "complete.obs")

empathy_cor <- data.frame(empathy_cor) |>
  rownames_to_column(var = "empathy_scale") |>
  mutate(across(
    .cols = -empathy_scale,
    .fns = ~if_else(abs(.x) > .20, .x, 0) #coercing anything less than a small correlation to 0 for simplicity of viewing
  ))

#empathy_cor #see full matrix (with 0s)

empathy_cor_sig <- empathy_cor |>
  select(empathy_scale, comp_resource_total, comp_physical_selection)

tot_resource <- cor.test(seas2$EQ_total, seas2$comp_resource_total, exact = FALSE)

contagion_resource <- cor.test(seas2$EQ_contagion, seas2$comp_resource_total, exact = FALSE) #this follow-up test was not significant/above .20, even though the initial correlation table showed it to be

tot_phys <- cor.test(seas2$EQ_total, seas2$comp_physical_selection, exact = FALSE)

attention_phys <- cor.test(seas2$EQ_attention, seas2$comp_physical_selection, exact = FALSE)
```

The only relationships that displayed at least a weak correlation (absolute value >= .20) were EmQue total x comparison resource selection (r = `r signif(unname(tot_resource$estimate), 2)` (weak negative), p = `r signif(unname(tot_resource$p.value), 2)`), EmQue total x comparison physical resource selection (r = `r signif(unname(tot_phys$estimate), 2)` (weak negative), p = `r signif(unname(tot_phys$p.value), 2)`), and EmQue attention x comparison physical resource selection (r = `r signif(unname(attention_phys$estimate), 2)` (weak negative), p = `r signif(unname(attention_phys$p.value), 2)`).

When a Bonferroni correction was applied to account for the 36 exploratory correlations calculated here, none of the above associations remained significant, p~total_resource~ = `r signif(unname(tot_resource$p.value), 2) * 36`, p~total_physical~ = `r signif(unname(tot_phys$p.value), 2) * 36`, p~attention_physical~ = `r signif(unname(attention_phys$p.value), 2) * 36`.